---
title: "Survival analysis -- all pipelines, POP, OAK, IMP130"
author: "Xiao Li"
date: "12/01/2022"
output: 
  html_document:
    toc: yes
    toc_depth: 2
    number_sections: TRUE
    code_folding: hide
pkgdown:
  as_is: true
vignette: >
  %\VignetteIndexEntry{Risk factors for critical illness}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, dpi = 100, fig.width = 8, fig.height = 8)
```


# load dependencies
```{r, warning=F}
rm(list = ls())

library('uwot')
library('dplyr')
select <- dplyr::select
library('ggplot2')
library('survival')
library("survminer")
library('openxlsx')
library('caret')
library('tidyverse')
library('rpart')
library('rpart.plot')
library('randomForest')
library('e1071')
library('openxlsx')
library('pROC')

custom_theme <- function() {
  theme_survminer() %+replace%
    theme(
      plot.title=element_text(hjust=0.5)
    )
}

seed = 42
set.seed(seed)

```


# training using POPLAR dataset
```{r}
if (file.exists('~/Automated_Immunophenotyping/JPATH/pop_trn_model_pip4_tuneRF.RData')){
  load('~/Automated_Immunophenotyping/JPATH/pop_trn_model_pip4_tuneRF.RData')
} else {
  load("~/Automated_Immunophenotyping/HK_POPLAR_alltiles_100_cutoff=0.25.RData")
  comb_res = comb_res[, -which(colnames(comb_res) == "ID")[1]]
  
  POP_manual = read.csv('~/Automated_Immunophenotyping/POPLAR_with_BCOR.csv')[, c("ID", "immunophenotype")]
  
  Xiao_dat = merge(comb_res, POP_manual, by = "ID")
  
  Xiao_dat = Xiao_dat[!is.na(Xiao_dat$immunophenotype),]
  
  
  Jeff_POP = read.xlsx('~/Automated_Immunophenotyping/20220211_poplar_bins.xlsx', sheet = 2)
  Jeff_POP$ID = paste0(Jeff_POP$Sample.ID, '_', Jeff_POP$StarLiMS.ID, '_ckpos_tiles.csv')
  Jeff_POP = Jeff_POP[, c(35, 16:24, 26:34, 12)]
  
  combine_POP = Jeff_POP %>% inner_join(Xiao_dat %>% select(-"immunophenotype"), by = "ID") %>% select(-"ID")
  
  
  #5 folds repeat 10 times
  control <- trainControl(method = 'repeatedcv', 
                          number = 5, 
                          repeats = 3,
                          search = "grid")
    
  
  #Number randomely variable selected is mtry
  mtry <- round(sqrt(ncol(combine_POP)-1))
  tunegrid <- expand.grid(.mtry = c((mtry-1):(mtry+5)),
                          .min.node.size = c(1:5),
                          .splitrule = "gini")
  modellist <- list()
  
  ntree_candidates <- c(100, 150, 200, 250, 300, 350, 400, 450, 500)
  for (ntree in ntree_candidates){
    set.seed(seed)
    rf_training <- train(Manual_Immunophenotype ~ ., 
                       data = combine_POP, 
                       method = 'ranger', 
                       preProcess = NULL,
                       num.trees = ntree,
                       tuneGrid = tunegrid, 
                       trControl = control)
  
    key <- toString(ntree)
    modellist[[key]] <- rf_training
  }
  
  
  
  results <- resamples(modellist)
  summary(results)
  
  best_id = which.max(as.data.frame(summary(results)$statistics$Accuracy)$Mean)
  
  best_ntree = ntree_candidates[best_id]
  
  best_res = modellist[[best_id]]$results
  
  set.seed(seed)
  rf_training <- train(Manual_Immunophenotype ~ ., 
                       data = combine_POP, 
                       method = 'ranger', 
                       preProcess = NULL,
                       num.trees = best_ntree,
                       tuneGrid = expand.grid(mtry = best_res$mtry[which.max(best_res$Accuracy)],
                                              min.node.size = best_res$min.node.size[which.max(best_res$Accuracy)], 
                                              splitrule = best_res$splitrule[which.max(best_res$Accuracy)]),
                       trControl = trainControl(classProbs = TRUE)
                       )
  
  print(rf_training$results)
  
  save(rf_training, file = "~/Automated_Immunophenotyping/JPATH/pop_trn_model_pip4_tuneRF.RData")

}



# rfImp = varImp(rf_training, scale = F)
# plot(rfImp, top = 20) 


```


### evaluation metrics
```{r}

multi_class_metrics <- function(pred, y_true){
  
                        y_pred = factor(c("Desert", "Excluded", "Inflamed")[apply(pred, 1, which.max)], levels = c("Inflamed", "Excluded", "Desert"))
                        cm <- as.matrix(confusionMatrix(y_pred, y_true))
                        n = sum(cm) # number of instances
                        nc = nrow(cm) # number of classes
                        rowsums = apply(cm, 1, sum) # number of instances per class
                        colsums = apply(cm, 2, sum) # number of predictions per class
                        diag = diag(cm)  # number of correctly classified instances per class 

                        precision = diag / colsums 
                        recall = diag / rowsums 
                        f1 = 2 * precision * recall / (precision + recall) 
                        
                        print(" ************ Confusion Matrix ************")
                        print(cm)
                        print(" ************ Diag ************")
                        print(diag)
                        print(" ************ Precision/Recall/F1 ************")
                        print(data.frame(precision, recall, f1)) 
                        
                        macroPrecision = mean(precision)
                        macroRecall = mean(recall)
                        macroF1 = mean(f1)
                        
                        print(" ************ Macro Precision/Recall/F1 ************")
                        print(data.frame(macroPrecision, macroRecall, macroF1)) 

                        
                        print(" ************ AUC ************")
                        roc.multi <- multiclass.roc(response = y_true, predictor = pred[, c(3,2,1)], plot = FALSE, quiet = TRUE)
                        print(auc(roc.multi))
                        
                      }


```



# harmonize different data source for OAK, we include the subject with multiple sample but concordant IP calls
```{r, warning = F}
load("~/Automated_Immunophenotyping/HK_OAK_alltiles_100_cutoff=0.25.RData")
Xiao_OAK = comb_res[, -which(colnames(comb_res) == "ID")[1]]

Jeff_OAK = readxl::read_excel('~/Automated_Immunophenotyping/COLLATE_OAK_HK_final_20220606153656.xlsx', sheet = 1, col_types = c(rep("text", 10), rep("numeric", 27))) %>% mutate(Final.call = `Final consensus manual phenotype`)

Jeff_OAK$ID = paste0(Jeff_OAK$Sample.ID, '_', Jeff_OAK$StarLiMS.ID, '_ckpos_tiles.csv')

Hauke_dat = read.csv('~/Automated_Immunophenotyping/Patient-MetaData_GO28915_OAK_v070_2112120_for-Darya - PatientDataTable_GO28915_OAK_new_210828.csv')

combine_OAK = Xiao_OAK %>% inner_join(Jeff_OAK[, c(4,2,3, 18:39)], by = "ID") %>%
                inner_join(Hauke_dat %>% select(USUBJID, ACTARM, OS_MONTHS, OS_CENSOR, PFS_MONTHS, PFS_CENSOR), by = "USUBJID")  %>% 
                mutate(Final.call = factor(Final.call, levels = c("Inflamed", "Excluded", "Desert")))


fea = names(rf_training$trainingData)[-which(names(rf_training$trainingData) == ".outcome")]

names(combine_OAK)[55:74] = gsub(" ", ".", names(combine_OAK)[55:74])

combine_OAK = combine_OAK[complete.cases(combine_OAK), ] %>% unique()
```


# prediction on OAK (combing arms)
```{r}
pred <- predict(rf_training, 
                combine_OAK[, fea], 
                type = "prob")

xtab = table(factor(c("Desert", "Excluded", "Inflamed")[apply(pred, 1, which.max)], levels = c("Inflamed", "Excluded", "Desert"))
, combine_OAK$Final.call)

print(paste0("Classification accuracy is ", sum(diag(xtab))/sum(xtab)))

vcd::Kappa(xtab)
xtab

combine_OAK$combined = factor(c("Desert", "Excluded", "Inflamed")[apply(pred, 1, which.max)], levels = c("Inflamed", "Excluded", "Desert"))
multi_class_metrics(pred = pred,
                    y_true = combine_OAK$Final.call)


pip4_pred_OAK = data.frame("ID" = combine_OAK %>% select(ID), "ACTARM" = combine_OAK$ACTARM, "MOCHA_BITE" = combine_OAK$combined, "Manual" = combine_OAK$Final.call)

write.csv(pip4_pred_OAK, '~/Automated_Immunophenotyping/JPATH/pip4_pred_OAK.csv', row.names = F)
```


```{r}
## the generic plotting function

surv_plot <- function(fit_obj = fit_combined, data = A_dat, time = "OS_MONTHS", cen = "OS_CENSOR", method = "combined", title = "OS for Atezolizumab by \nMOCHA-BITE method", 
                      hjust1 = 0, hjust2 = -0.2, hjust3 = 1){
  
  p_combined_A_OS = ggsurvplot(fit_obj, data = data, palette = COLOR, 
                               size = 0.4, 
                               censor.size = 2.5,
                               font.main = c(8, "bold"), 
                               legend.title = "Immunophenotyping",
                               legend.labs = c("Inflamed", "Excluded", "Desert"),
                               font.legend = 6,
                               conf.int = F,          # Add confidence interval
                               pval = FALSE,              # Add p-value
                               risk.table = TRUE,  
                               risk.table.fontsize = 1.6,
                               title = title, 
                               ggtheme=custom_theme(),
                               font.x = 7,
                               font.y = 7,
                               font.tickslab = 5,
                               surv.median.line = "hv", 
                               tables.theme = theme_cleantable(), 
                               axes.offset = F, 
                               xlim = c(0, ceiling(max(data[[time]]))))

  p_combined_A_OS$table <- p_combined_A_OS$table +
                              theme(plot.title = element_text(size = 7, face = "bold"))
  p_combined_A_OS$table$theme$axis.text.y$size = 6

  p_val = survdiff(as.formula(paste0("Surv(", time, "," , cen, ") ~ " , method)), data = data)
  p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5)
  
  med_time = surv_median(fit_obj)[,2]
  
  p_combined_A_OS$plot <- p_combined_A_OS$plot +
    annotate("text", size = 2.5, x = 0.8*max(data[[time]]), y = 0.6, label = paste0("p=", p_val), cex=5, col="black", vjust=0, hjust = 1.1, fontface=1) + 
    annotate("text", size = 2.5, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=5, col=COLOR[1], vjust=0, hjust = hjust1, fontface=1) + 
    annotate("text", size = 2.5, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=5, col=COLOR[2], vjust=0, hjust = hjust2, fontface=1) + 
    annotate("text", size = 2.5, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=5, col=COLOR[3], vjust=0, hjust = hjust3, fontface=1)
  
  return(p_combined_A_OS)
  
}

```



# OS Survival analysis (OAK)
```{r}
COLOR <- c("#ED7D31", "#4472C4", "#A5A5A5")

A_dat = combine_OAK %>% filter(ACTARM == "atezo")
D_dat = combine_OAK %>% filter(ACTARM == "doce") 


A_dat = A_dat %>% select(combined, Final.call, OS_MONTHS, OS_CENSOR, PFS_MONTHS, PFS_CENSOR)

D_dat = D_dat %>% select(combined, Final.call, OS_MONTHS, OS_CENSOR, PFS_MONTHS, PFS_CENSOR)
#######################################################################################################
########################        OS for cut-off, SVM, MOCHA and Manuals       ########################
#######################################################################################################

## Atezo arm

fit_combined <- survfit(Surv(OS_MONTHS, OS_CENSOR) ~ combined, data = A_dat)
fit_manual <- survfit(Surv(OS_MONTHS, OS_CENSOR) ~ Final.call, data = A_dat)


p_combined_A_OS = surv_plot(fit_obj = fit_combined, data = A_dat, time = "OS_MONTHS", cen = "OS_CENSOR", method = "combined", title = "OS for Atezolizumab by \nMOCHA-BITE method",
                            hjust1 = 0, hjust2 = -0.2, hjust3 = 1)
# p_combined_A_OS = ggsurvplot(fit_combined, data = A_dat, palette = COLOR, size = 2, 
#                 font.main = c(18, "bold"), legend.title = "Immunophenotyping",
#                 legend.labs = c("Inflamed", "Excluded", "Desert"),
#                 conf.int = F,          # Add confidence interval
#                 pval = FALSE,              # Add p-value
#                 risk.table = TRUE,  title = "OS for Atezolizumab by MOCHA-BITE method", ggtheme=custom_theme(),
#                 surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS))))
# 
# 
# 
# p_val = survdiff(Surv(OS_MONTHS, OS_CENSOR) ~ combined, data = A_dat)
# p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5)
# 
# med_time = surv_median(fit_combined)[,2]
# 
# p_combined_A_OS$plot <- p_combined_A_OS$plot +
#   annotate("text", size = 7, x = 28, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) + 
#   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = 0, fontface=1) + 
#   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = -0.2, fontface=1) + 
#   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 1.5, fontface=1)
# 
# print(p_combined_A_OS)



p_manual_A_OS = surv_plot(fit_obj = fit_manual, data = A_dat, time = "OS_MONTHS", cen = "OS_CENSOR", method = "Final.call", title = "OS for Atezolizumab by \nManual method", 
                          hjust1 = 0.2, hjust2 = 1, hjust3 = 0)
# p_manual_A_OS = ggsurvplot(fit_manual, data = A_dat, palette = COLOR, size = 2, 
#                 font.main = c(18, "bold"), legend.title = "Immunophenotyping", 
#                 legend.labs = c("Inflamed", "Excluded", "Desert"), 
#                 conf.int = F,          # Add confidence interval
#                 pval = FALSE,              # Add p-value
#                 risk.table = TRUE,  title = "OS for Atezolizumab by Manual method", ggtheme=custom_theme(),
#                 surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS))))
# 
# p_val = survdiff(Surv(OS_MONTHS, OS_CENSOR) ~ Final.call, data = A_dat)
# p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5)
# 
# med_time = surv_median(fit_manual)[,2]
# 
# p_manual_A_OS$plot <- p_manual_A_OS$plot +
#   annotate("text", size = 7, x = 28, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) + 
#   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = 0.2, fontface=1) + 
#   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 1, fontface=1) + 
#   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = -0.6, fontface=1)
# 
# print(p_manual_A_OS)





## Doce arm

fit_combined <- survfit(Surv(OS_MONTHS, OS_CENSOR) ~ combined, data = D_dat)
fit_manual <- survfit(Surv(OS_MONTHS, OS_CENSOR) ~ Final.call, data = D_dat)


p_combined_D_OS = surv_plot(fit_obj = fit_combined, data = D_dat, time = "OS_MONTHS", cen = "OS_CENSOR", method = "combined", title = "OS for Docetaxel by \nMOCHA-BITE method", 
                          hjust1 = 1, hjust2 = -2, hjust3 = 2)
# p_combined_D_OS = ggsurvplot(fit_combined, data = D_dat, palette = COLOR, size = 2, 
#                              font.main = c(18, "bold"), legend.title = "Immunophenotyping",
#                              legend.labs = c("Inflamed", "Excluded", "Desert"),
#                              conf.int = F,          # Add confidence interval
#                              pval = FALSE,              # Add p-value
#                              risk.table = TRUE,  title = "OS for Docetaxel by MOCHA-BITE method", ggtheme=custom_theme(),
#                              surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(D_dat$OS_MONTHS))))
# 
# p_val = survdiff(Surv(OS_MONTHS, OS_CENSOR) ~ combined, data = D_dat)
# p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5)
# 
# med_time = surv_median(fit_combined)[,2]
# 
# p_combined_D_OS$plot <- p_combined_D_OS$plot +
#   annotate("text", size = 7, x = 28, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) + 
#   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[2], vjust=0, hjust = 1, fontface=1) + 
#   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[1], vjust=0, hjust = -2, fontface=1) + 
#   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 2, fontface=1)
# 
# print(p_combined_D_OS)



p_manual_D_OS = surv_plot(fit_obj = fit_manual, data = D_dat, time = "OS_MONTHS", cen = "OS_CENSOR", method = "Final.call", title = "OS for Docetaxel by \nManual method", 
                          hjust1 = 0, hjust2 = -1.5, hjust3 = 1.5)
# p_manual_D_OS = ggsurvplot(fit_manual, data = D_dat, palette = COLOR, size = 2, 
#                            font.main = c(18, "bold"), legend.title = "Immunophenotyping", 
#                            legend.labs = c("Inflamed", "Excluded", "Desert"), 
#                            conf.int = F,          # Add confidence interval
#                            pval = FALSE,              # Add p-value
#                            risk.table = TRUE,  title = "OS for Docetaxel by Manual method", ggtheme=custom_theme(),
#                            surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(D_dat$OS_MONTHS))))
# 
# p_val = survdiff(Surv(OS_MONTHS, OS_CENSOR) ~ Final.call, data = D_dat)
# p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5)
# 
# med_time = surv_median(fit_manual)[,2]
# 
# p_manual_D_OS$plot <- p_manual_D_OS$plot +
#   annotate("text", size = 7, x = 28, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) + 
#   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) + 
#   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[1], vjust=0, hjust = -1.5, fontface=1) + 
#   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 1.5, fontface=1)
# 
# print(p_manual_D_OS)


```



# PFS Survival analysis (OAK)
```{r}

#######################################################################################################
########################        PFS for cut-off, SVM, MOCHA and Manuals       ########################
#######################################################################################################

## Atezo arm

fit_combined <- survfit(Surv(PFS_MONTHS, PFS_CENSOR) ~ combined, data = A_dat)
fit_manual <- survfit(Surv(PFS_MONTHS, PFS_CENSOR) ~ Final.call, data = A_dat)


p_combined_A_PFS = surv_plot(fit_obj = fit_combined, data = A_dat, time = "PFS_MONTHS", cen = "PFS_CENSOR", method = "combined", title = "PFS for Atezolizumab by \nMOCHA-BITE method", 
                          hjust1 = -2, hjust2 = -1, hjust3 = 0)
# p_combined_A_PFS = ggsurvplot(fit_combined, data = A_dat, palette = COLOR, size = 2, 
#                              font.main = c(18, "bold"), legend.title = "Immunophenotyping",
#                              legend.labs = c("Inflamed", "Excluded", "Desert"),
#                              conf.int = F,          # Add confidence interval
#                              pval = FALSE,              # Add p-value
#                              risk.table = TRUE,  title = "PFS for Atezolizumab by MOCHA-BITE method", ggtheme=custom_theme(),
#                              surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$PFS_MONTHS))))
# 
# p_val = survdiff(Surv(PFS_MONTHS, PFS_CENSOR) ~ combined, data = A_dat)
# p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5)
# 
# med_time = surv_median(fit_combined)[,2]
# 
# p_combined_A_PFS$plot <- p_combined_A_PFS$plot +
#   annotate("text", size = 7, x = 28, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) + 
#   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -2, fontface=1) + 
#   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = -0.5, fontface=1) + 
#   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 1.5, fontface=1)
# 
# print(p_combined_A_PFS)



p_manual_A_PFS = surv_plot(fit_obj = fit_manual, data = A_dat, time = "PFS_MONTHS", cen = "PFS_CENSOR", method = "Final.call", title = "PFS for Atezolizumab by \nManual method", 
                          hjust1 = -7, hjust2 = -2, hjust3 = -1)
# p_manual_A_PFS = ggsurvplot(fit_manual, data = A_dat, palette = COLOR, size = 2, 
#                            font.main = c(18, "bold"), legend.title = "Immunophenotyping", 
#                            legend.labs = c("Inflamed", "Excluded", "Desert"), 
#                            conf.int = F,          # Add confidence interval
#                            pval = FALSE,              # Add p-value
#                            risk.table = TRUE,  title = "PFS for Atezolizumab by Manual method", ggtheme=custom_theme(),
#                            surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$PFS_MONTHS))))
# 
# p_val = survdiff(Surv(PFS_MONTHS, PFS_CENSOR) ~ Final.call, data = A_dat)
# p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5)
# 
# med_time = surv_median(fit_manual)[,2]
# 
# p_manual_A_PFS$plot <- p_manual_A_PFS$plot +
#   annotate("text", size = 7, x = 28, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) + 
#   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -1, fontface=1) + 
#   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) + 
#   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 2, fontface=1)
# 
# print(p_manual_A_PFS)





## Doce arm

fit_combined <- survfit(Surv(PFS_MONTHS, PFS_CENSOR) ~ combined, data = D_dat)
fit_manual <- survfit(Surv(PFS_MONTHS, PFS_CENSOR) ~ Final.call, data = D_dat)

p_combined_D_PFS = surv_plot(fit_obj = fit_combined, data = D_dat, time = "PFS_MONTHS", cen = "PFS_CENSOR", method = "combined", title = "PFS for Docetaxel by \nMOCHA-BITE method", 
                          hjust1 = -2, hjust2 = -1, hjust3 = 0)
# p_combined_D_PFS = ggsurvplot(fit_combined, data = D_dat, palette = COLOR, size = 2, 
#                              font.main = c(18, "bold"), legend.title = "Immunophenotyping",
#                              legend.labs = c("Inflamed", "Excluded", "Desert"),
#                              conf.int = F,          # Add confidence interval
#                              pval = FALSE,              # Add p-value
#                              risk.table = TRUE,  title = "PFS for Docetaxel by MOCHA-BITE method", ggtheme=custom_theme(),
#                              surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(D_dat$PFS_MONTHS))))
# 
# p_val = survdiff(Surv(PFS_MONTHS, PFS_CENSOR) ~ combined, data = D_dat)
# p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5)
# 
# med_time = surv_median(fit_combined)[,2]
# 
# p_combined_D_PFS$plot <- p_combined_D_PFS$plot +
#   annotate("text", size = 7, x = 28, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) + 
#   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -1, fontface=1) + 
#   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) + 
#   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 1, fontface=1)
# 
# print(p_combined_D_PFS)



p_manual_D_PFS = surv_plot(fit_obj = fit_manual, data = D_dat, time = "PFS_MONTHS", cen = "PFS_CENSOR", method = "Final.call", title = "PFS for Docetaxel by \nManual method", 
                          hjust1 = -2, hjust2 = 0, hjust3 = 0.5)
# p_manual_D_PFS = ggsurvplot(fit_manual, data = D_dat, palette = COLOR, size = 2, 
#                            font.main = c(18, "bold"), legend.title = "Immunophenotyping", 
#                            legend.labs = c("Inflamed", "Excluded", "Desert"), 
#                            conf.int = F,          # Add confidence interval
#                            pval = FALSE,              # Add p-value
#                            risk.table = TRUE,  title = "PFS for Docetaxel by Manual method", ggtheme=custom_theme(),
#                            surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(D_dat$PFS_MONTHS))))
# 
# p_val = survdiff(Surv(PFS_MONTHS, PFS_CENSOR) ~ Final.call, data = D_dat)
# p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5)
# 
# med_time = surv_median(fit_manual)[,2]
# 
# p_manual_D_PFS$plot <- p_manual_D_PFS$plot +
#   annotate("text", size = 7, x = 28, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) + 
#   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -2, fontface=1) + 
#   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) + 
#   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 0.5, fontface=1)
# 
# print(p_manual_D_PFS)
```


```{r}

splots <- list()
splots[[1]] <- p_combined_A_OS
splots[[2]] <- p_manual_A_OS
splots[[3]] <- p_combined_D_OS
splots[[4]] <- p_manual_D_OS

splots[[5]] <- p_combined_A_PFS
splots[[6]] <- p_manual_A_PFS
splots[[7]] <- p_combined_D_PFS
splots[[8]] <- p_manual_D_PFS


png("~/Automated_Immunophenotyping/JPATH/OS_comp_new_preferred_OAK_pip4.png", width = 17, height = 14, res = 300, units = "cm")
# Arrange multiple ggsurvplots and print the output
arrange_ggsurvplots(list(splots[[1]], splots[[3]], splots[[2]], splots[[4]]), print = TRUE,
                    ncol = 2, nrow = 2, risk.table.height = 0.2)
dev.off()


png("~/Automated_Immunophenotyping/JPATH/PFS_comp_new_preferred_OAK_pip4.png", width = 17, height = 14, res = 300, units = "cm")
# Arrange multiple ggsurvplots and print the output
arrange_ggsurvplots(list(splots[[5]], splots[[7]], splots[[6]], splots[[8]]), print = TRUE,
                    ncol = 2, nrow = 2, risk.table.height = 0.2)
dev.off()


```



# prediction on IMPassion130 (combing arms)
```{r, warning=FALSE}
Jeff_IMP130 = readxl::read_xlsx('~/Automated_Immunophenotyping/20221002_IMP130_tracker.xlsx', sheet = 1, col_types = c(rep("text", 12), rep("numeric", 27))) %>% mutate(Final.call = factor(Immunophenotype_HK, levels = c("Inflamed", "Excluded", "Desert")))
Jeff_IMP130 = Jeff_IMP130[-c(1:8, 10, 11, 14, 16, 17), ]
Jeff_IMP130$ID = paste0(Jeff_IMP130$Block, '_', as.numeric(Jeff_IMP130$`Patient Number`), '_ckpos_tiles.csv')
Jeff_IMP130 = Jeff_IMP130[, c(21:29, 31:39, 40, 41)]; names(Jeff_IMP130)[1:18] = gsub(" ", ".", names(Jeff_IMP130)[1:18])

Xiao_IMP130 = read.csv('~/Automated_Immunophenotyping/IMPassion130_res.csv'); Xiao_IMP130 = Xiao_IMP130[, -which(colnames(Xiao_IMP130) == "ID.1")[1]]

# Jeff_IMP130$ID[!(Jeff_IMP130$ID %in% Xiao_IMP130$ID)] 
# "HP-208267_1175_ckpos_tiles.csv" "HP-208290_1209_ckpos_tiles.csv" "HP-208637_1517_ckpos_tiles.csv" 
# these 3 files are either short of pos tiles or neg tiles

combine_IMP130 = merge(Jeff_IMP130, Xiao_IMP130, by = "ID")
combine_IMP130 = combine_IMP130[complete.cases(combine_IMP130),]



```


```{r}

tmp1 = read.csv('~/Automated_Immunophenotyping/20221002_IMP130_tracker_ANON.csv') %>% select(uni_id = hashed.uniId, HK_block = 'Specimen.._HK')
tmp2 = read.csv('~/Automated_Immunophenotyping/wo29522_clin_jea_hk_10022022.csv')

tmp3 = merge(tmp1, tmp2, by = "uni_id")

# combine_IMP130 = combine_IMP130 %>% mutate(HK_block = substr(ID, 1, 9),
#                                      combined = factor(c("Desert", "Excluded", "Inflamed")[apply(pred, 1, which.max)], levels = c("Inflamed", "Excluded", "Desert"))) %>% 
#                                      select(HK_block, Final.call, combined)

dat_IMP130 = merge(combine_IMP130 %>% mutate(HK_block = substr(ID, 1, 9)), 
                   tmp3, 
                   by = "HK_block") %>% unique()


pred <- predict(rf_training, 
                dat_IMP130[, fea], 
                type = "prob")

xtab = table(factor(c("Desert", "Excluded", "Inflamed")[apply(pred, 1, which.max)], levels = c("Inflamed", "Excluded", "Desert"))
, dat_IMP130$Final.call)

print(paste0("Classification accuracy is ", sum(diag(xtab))/sum(xtab)))

vcd::Kappa(xtab)
xtab

multi_class_metrics(pred = pred,
                    y_true = dat_IMP130$Final.call)


dat_IMP130$combined = factor(c("Desert", "Excluded", "Inflamed")[apply(pred, 1, which.max)], levels = c("Inflamed", "Excluded", "Desert"))



pip4_pred_IMP130 = data.frame("ID" = dat_IMP130 %>% select(ID), "ACTARM" = dat_IMP130$arm, "MOCHA_BITE" = dat_IMP130$combined, "Manual" = dat_IMP130$Final.call)

write.csv(pip4_pred_IMP130, '~/Automated_Immunophenotyping/JPATH/pip4_pred_IMP130.csv', row.names = F)
```



# OS Survival analysis (IMPassion130)
```{r}
COLOR <- c("#ED7D31", "#4472C4", "#A5A5A5")

A_dat = dat_IMP130 %>% filter(arm == "MPDL3280A")

D_dat = dat_IMP130 %>% filter(arm == "PLACEBO")
#######################################################################################################
########################            OS for combined and Manuals         ########################
#######################################################################################################

## Atezo arm
fit_combined <- survfit(Surv(os_months, 1-os_cnsr) ~ combined, data = A_dat)
fit_manual <- survfit(Surv(os_months, 1-os_cnsr) ~ Final.call, data = A_dat)


p_comb_A_OS = surv_plot(fit_obj = fit_combined, data = A_dat, time = "os_months", cen = "1-os_cnsr", method = "combined", title = "OS for Atezolizumab by \nMOCHA-BITE method", 
                          hjust1 = -2, hjust2 = -1, hjust3 = 0)
# p_comb_A_OS = ggsurvplot(fit_combined, data = A_dat, palette = COLOR, size = 2, 
#                 font.main = c(18, "bold"), legend.title = "Immunophenotyping",
#                 legend.labs = c("Inflamed", "Excluded", "Desert"),
#                 conf.int = F,          # Add confidence interval
#                 pval = FALSE,              # Add p-value
#                 risk.table = TRUE,  title = "OS for Atezolizumab by MOCHA-BITE method", ggtheme=custom_theme(),
#                 surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$os_months))))
# 
# p_val = survdiff(Surv(os_months, 1-os_cnsr) ~ combined, data = A_dat)
# p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5)
# 
# med_time = surv_median(fit_combined)[,2]
# 
# p_comb_A_OS$plot <- p_comb_A_OS$plot +
#   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) + 
#   annotate("text", size = 7, x = med_time[1], y = 0.6, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -1, fontface=1) + 
#   annotate("text", size = 7, x = med_time[2], y = 0.6, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) + 
#   annotate("text", size = 7, x = med_time[3], y = 0.6, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 3, fontface=1)
# 
# print(p_comb_A_OS)


p_manual_A_OS = surv_plot(fit_obj = fit_manual, data = A_dat, time = "os_months", cen = "1-os_cnsr", method = "Final.call", title = "OS for Atezolizumab by \nManual method", 
                          hjust1 = -1, hjust2 = 0.5, hjust3 = 0)
# p_manual_A_OS = ggsurvplot(fit_manual, data = A_dat, palette = COLOR, size = 2, 
#                 font.main = c(18, "bold"), legend.title = "Immunophenotyping", 
#                 legend.labs = c("Inflamed", "Excluded", "Desert"), 
#                 conf.int = F,          # Add confidence interval
#                 pval = FALSE,              # Add p-value
#                 risk.table = TRUE,  title = "OS for Atezolizumab by Manual method", ggtheme=custom_theme(),
#                 surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$os_months))))
# 
# p_val = survdiff(Surv(os_months, 1-os_cnsr) ~ Final.call, data = A_dat)
# p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5)
# 
# med_time = surv_median(fit_manual)[,2]
# 
# p_manual_A_OS$plot <- p_manual_A_OS$plot +
#   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) + 
#   annotate("text", size = 7, x = med_time[1], y = 0.6, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -1.5, fontface=1) + 
#   annotate("text", size = 7, x = med_time[2], y = 0.6, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) + 
#   annotate("text", size = 7, x = med_time[3], y = 0.6, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 2.5, fontface=1)
# 
# print(p_manual_A_OS)





## Placebo arm
fit_combined <- survfit(Surv(os_months, 1-os_cnsr) ~ combined, data = D_dat)
fit_manual <- survfit(Surv(os_months, 1-os_cnsr) ~ Final.call, data = D_dat)


p_comb_D_OS = surv_plot(fit_obj = fit_combined, data = D_dat, time = "os_months", cen = "1-os_cnsr", method = "combined", title = "OS for Placebo by \nMOCHA-BITE method", 
                          hjust1 = 1.8, hjust2 = 0.5, hjust3 = -1.5)
# p_comb_D_OS = ggsurvplot(fit_combined, data = D_dat, palette = COLOR, size = 2, 
#                 font.main = c(18, "bold"), legend.title = "Immunophenotyping",
#                 legend.labs = c("Inflamed", "Excluded", "Desert"),
#                 conf.int = F,          # Add confidence interval
#                 pval = FALSE,              # Add p-value
#                 risk.table = TRUE,  title = "OS for Placebo by MOCHA-BITE method", ggtheme=custom_theme(),
#                 surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(D_dat$os_months))))
# 
# p_val = survdiff(Surv(os_months, 1-os_cnsr) ~ combined, data = D_dat)
# p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5)
# 
# med_time = surv_median(fit_combined)[,2]
# 
# p_comb_D_OS$plot <- p_comb_D_OS$plot +
#   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) + 
#   annotate("text", size = 7, x = med_time[1], y = 0.6, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = 3, fontface=1) + 
#   annotate("text", size = 7, x = med_time[2], y = 0.6, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0.5, fontface=1) + 
#   annotate("text", size = 7, x = med_time[3], y = 0.6, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = -1.5, fontface=1)
# 
# print(p_comb_D_OS)


p_manual_D_OS = surv_plot(fit_obj = fit_manual, data = D_dat, time = "os_months", cen = "1-os_cnsr", method = "Final.call", title = "OS for Placebo by \nManual method", 
                          hjust1 = 1.8, hjust2 = 0, hjust3 = -2)
# p_manual_D_OS = ggsurvplot(fit_manual, data = D_dat, palette = COLOR, size = 2, 
#                 font.main = c(18, "bold"), legend.title = "Immunophenotyping", 
#                 legend.labs = c("Inflamed", "Excluded", "Desert"), 
#                 conf.int = F,          # Add confidence interval
#                 pval = FALSE,              # Add p-value
#                 risk.table = TRUE,  title = "OS for Placebo by Manual method", ggtheme=custom_theme(),
#                 surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(D_dat$os_months))))
# 
# p_val = survdiff(Surv(os_months, 1-os_cnsr) ~ Final.call, data = D_dat)
# p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5)
# 
# med_time = surv_median(fit_manual)[,2]
# 
# p_manual_D_OS$plot <- p_manual_D_OS$plot +
#   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) + 
#   annotate("text", size = 7, x = med_time[1], y = 0.6, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = 3, fontface=1) + 
#   annotate("text", size = 7, x = med_time[2], y = 0.6, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) + 
#   annotate("text", size = 7, x = med_time[3], y = 0.6, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = -2, fontface=1)
# 
# print(p_manual_D_OS)

```



# PFS Survival analysis (IMPassion130)
```{r}

#######################################################################################################
########################            PFS for combined and Manuals         ########################
#######################################################################################################

## Atezo arm
fit_combined <- survfit(Surv(pfs_months, 1-pfs_cnsr) ~ combined, data = A_dat)
fit_manual <- survfit(Surv(pfs_months, 1-pfs_cnsr) ~ Final.call, data = A_dat)


p_comb_A_pfs = surv_plot(fit_obj = fit_combined, data = A_dat, time = "pfs_months", cen = "1-pfs_cnsr", method = "combined", title = "PFS for Atezolizumab by \nMOCHA-BITE  method", 
                          hjust1 = -4.5, hjust2 = -2.5, hjust3 = -0.5)
# p_comb_A_pfs = ggsurvplot(fit_combined, data = A_dat, palette = COLOR, size = 2, 
#                          font.main = c(18, "bold"), legend.title = "Immunophenotyping",
#                          legend.labs = c("Inflamed", "Excluded", "Desert"),
#                          conf.int = F,          # Add confidence interval
#                          pval = FALSE,              # Add p-value
#                          risk.table = TRUE,  title = "PFS for Atezolizumab by MOCHA-BITE method", ggtheme=custom_theme(),
#                          surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$pfs_months))))
# 
# p_val = survdiff(Surv(pfs_months, 1-pfs_cnsr) ~ combined, data = A_dat)
# p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5)
# 
# med_time = surv_median(fit_combined)[,2]
# 
# p_comb_A_pfs$plot <- p_comb_A_pfs$plot +
#   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) + 
#   annotate("text", size = 7, x = med_time[1], y = 0.6, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -1.5, fontface=1) + 
#   annotate("text", size = 7, x = med_time[2], y = 0.6, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) + 
#   annotate("text", size = 7, x = med_time[3], y = 0.6, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 2.5, fontface=1)
# 
# print(p_comb_A_pfs)


p_manual_A_pfs = surv_plot(fit_obj = fit_manual, data = A_dat, time = "pfs_months", cen = "1-pfs_cnsr", method = "Final.call", title = "PFS for Atezolizumab by \nManual  method", 
                          hjust1 = -4.5, hjust2 = -2.5, hjust3 = -0.5)
# p_manual_A_pfs = ggsurvplot(fit_manual, data = A_dat, palette = COLOR, size = 2, 
#                            font.main = c(18, "bold"), legend.title = "Immunophenotyping", 
#                            legend.labs = c("Inflamed", "Excluded", "Desert"), 
#                            conf.int = F,          # Add confidence interval
#                            pval = FALSE,              # Add p-value
#                            risk.table = TRUE,  title = "PFS for Atezolizumab by Manual method", ggtheme=custom_theme(),
#                            surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$pfs_months))))
# 
# p_val = survdiff(Surv(pfs_months, 1-pfs_cnsr) ~ Final.call, data = A_dat)
# p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5)
# 
# med_time = surv_median(fit_manual)[,2]
# 
# p_manual_A_pfs$plot <- p_manual_A_pfs$plot +
#   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) + 
#   annotate("text", size = 7, x = med_time[1], y = 0.6, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -1.5, fontface=1) + 
#   annotate("text", size = 7, x = med_time[2], y = 0.6, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) + 
#   annotate("text", size = 7, x = med_time[3], y = 0.6, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 2.5, fontface=1)
# 
# print(p_manual_A_pfs)





## Placebo arm
fit_combined <- survfit(Surv(pfs_months, 1-pfs_cnsr) ~ combined, data = D_dat)
fit_manual <- survfit(Surv(pfs_months, 1-pfs_cnsr) ~ Final.call, data = D_dat)


p_comb_D_pfs = surv_plot(fit_obj = fit_combined, data = D_dat, time = "pfs_months", cen = "1-pfs_cnsr", method = "combined", title = "PFS for Placebo by \nMOCHA-BITE  method", 
                          hjust1 = -0.5, hjust2 = -2.5, hjust3 = -4.5)
# p_comb_D_pfs = ggsurvplot(fit_combined, data = D_dat, palette = COLOR, size = 2, 
#                          font.main = c(18, "bold"), legend.title = "Immunophenotyping",
#                          legend.labs = c("Inflamed", "Excluded", "Desert"),
#                          conf.int = F,          # Add confidence interval
#                          pval = FALSE,              # Add p-value
#                          risk.table = TRUE,  title = "PFS for Placebo by MOCHA-BITE method", ggtheme=custom_theme(),
#                          surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(D_dat$pfs_months))))
# 
# p_val = survdiff(Surv(pfs_months, 1-pfs_cnsr) ~ combined, data = D_dat)
# p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5)
# 
# med_time = surv_median(fit_combined)[,2]
# 
# p_comb_D_pfs$plot <- p_comb_D_pfs$plot +
#   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) + 
#   annotate("text", size = 7, x = med_time[1], y = 0.6, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = 2.5, fontface=1) + 
#   annotate("text", size = 7, x = med_time[2], y = 0.6, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = -0.5, fontface=1) + 
#   annotate("text", size = 7, x = med_time[3], y = 0.6, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = -2, fontface=1)
# 
# print(p_comb_D_pfs)



p_manual_D_pfs = surv_plot(fit_obj = fit_manual, data = D_dat, time = "pfs_months", cen = "1-pfs_cnsr", method = "Final.call", title = "PFS for Placebo by \nManual  method", 
                          hjust1 = -0.5, hjust2 = -2.5, hjust3 = -4.5)
# p_manual_D_pfs = ggsurvplot(fit_manual, data = D_dat, palette = COLOR, size = 2, 
#                            font.main = c(18, "bold"), legend.title = "Immunophenotyping", 
#                            legend.labs = c("Inflamed", "Excluded", "Desert"), 
#                            conf.int = F,          # Add confidence interval
#                            pval = FALSE,              # Add p-value
#                            risk.table = TRUE,  title = "PFS for Placebo by Manual method", ggtheme=custom_theme(),
#                            surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(D_dat$pfs_months))))
# 
# p_val = survdiff(Surv(pfs_months, 1-pfs_cnsr) ~ Final.call, data = D_dat)
# p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5)
# 
# med_time = surv_median(fit_manual)[,2]
# 
# p_manual_D_pfs$plot <- p_manual_D_pfs$plot +
#   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) + 
#   annotate("text", size = 7, x = med_time[1], y = 0.6, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = 2.5, fontface=1) + 
#   annotate("text", size = 7, x = med_time[2], y = 0.6, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = -0.5, fontface=1) + 
#   annotate("text", size = 7, x = med_time[3], y = 0.6, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = -2, fontface=1)
# 
# print(p_manual_D_pfs)

```





```{r}

splots <- list()
splots[[1]] <- p_comb_A_OS
splots[[2]] <- p_manual_A_OS
splots[[3]] <- p_comb_D_OS
splots[[4]] <- p_manual_D_OS

splots[[5]] <- p_comb_A_pfs
splots[[6]] <- p_manual_A_pfs
splots[[7]] <- p_comb_D_pfs
splots[[8]] <- p_manual_D_pfs


png("~/Automated_Immunophenotyping/JPATH/OS_comp_new_preferred_IMP130_pip4.png", width = 17, height = 14, res = 300, units = "cm")
# Arrange multiple ggsurvplots and print the output
arrange_ggsurvplots(list(splots[[1]], splots[[3]], splots[[2]], splots[[4]]), print = TRUE,
                    ncol = 2, nrow = 2, risk.table.height = 0.2)
dev.off()


png("~/Automated_Immunophenotyping/JPATH/PFS_comp_new_preferred_IMP130_pip4.png", width = 17, height = 14, res = 300, units = "cm")
# Arrange multiple ggsurvplots and print the output
arrange_ggsurvplots(list(splots[[5]], splots[[7]], splots[[6]], splots[[8]]), print = TRUE,
                    ncol = 2, nrow = 2, risk.table.height = 0.2)
dev.off()


```


































<!-- # training using POPLAR dataset -->
<!-- ```{r} -->
<!-- if (file.exists('~/Automated_Immunophenotyping/pop_trn_model_pip3.RData')){ -->
<!--   load('~/Automated_Immunophenotyping/pop_trn_model_pip3.RData') -->
<!-- } else { -->
<!--   load("~/Automated_Immunophenotyping/HK_POPLAR_alltiles_100_cutoff=0.25.RData") -->
<!--   comb_res = comb_res[, -which(colnames(comb_res) == "ID")[1]] -->

<!--   POP_manual = read.csv('POPLAR_with_BCOR.csv')[, c("ID", "immunophenotype")] -->

<!--   Xiao_dat = merge(comb_res, POP_manual, by = "ID") -->

<!--   Xiao_dat = Xiao_dat[!is.na(Xiao_dat$immunophenotype),] -->


<!--   Jeff_POP = read.xlsx('20220211_poplar_bins.xlsx', sheet = 2) -->
<!--   Jeff_POP$ID = paste0(Jeff_POP$Sample.ID, '_', Jeff_POP$StarLiMS.ID, '_ckpos_tiles.csv') -->
<!--   Jeff_POP = Jeff_POP[, c(35, 16:24, 26:34, 12)] -->

<!--   combine_POP = Jeff_POP %>% inner_join(Xiao_dat %>% select(-"immunophenotype"), by = "ID") %>% select(-"ID") -->
<!--   combine_POP = combine_POP[, 19:ncol(combine_POP)] -->

<!--   #5 folds repeat 10 times -->
<!--   control <- trainControl(method = 'repeatedcv',  -->
<!--                           number = 5,  -->
<!--                           repeats = 10) -->

<!--   #Number randomely variable selected is mtry -->
<!--   mtry <- round(sqrt(ncol(combine_POP)-1)) -->
<!--   tunegrid <- expand.grid(.mtry = mtry) -->

<!--   rf_training <- train(Manual_Immunophenotype ~ .,  -->
<!--                        data = combine_POP,  -->
<!--                        method = 'rf',  -->
<!--                        preProcess = NULL, -->
<!--                        ntree = 200, -->
<!--                        tuneGrid = tunegrid,  -->
<!--                        trControl = control) -->

<!--   save(rf_training, file = "~/Automated_Immunophenotyping/pop_trn_model_pip3.RData") -->
<!-- } -->

<!-- # rfImp = varImp(rf_training, scale = F) -->
<!-- # plot(rfImp, top = 20)  -->


<!-- ``` -->


<!-- # harmonize different data source for OAK, we include the subject with multiple sample but concordant IP calls -->
<!-- ```{r, warning = F} -->
<!-- load("~/Automated_Immunophenotyping/HK_OAK_alltiles_100_cutoff=0.25.RData") -->
<!-- Xiao_OAK = comb_res[, -which(colnames(comb_res) == "ID")[1]] -->

<!-- Jeff_OAK = readxl::read_excel('COLLATE_OAK_HK_final_20220606153656.xlsx', sheet = 1, col_types = c(rep("text", 10), rep("numeric", 27))) %>% mutate(Final.call = `Final consensus manual phenotype`) -->

<!-- Jeff_OAK$ID = paste0(Jeff_OAK$Sample.ID, '_', Jeff_OAK$StarLiMS.ID, '_ckpos_tiles.csv') -->

<!-- Hauke_dat = read.csv('Patient-MetaData_GO28915_OAK_v070_2112120_for-Darya - PatientDataTable_GO28915_OAK_new_210828.csv') -->

<!-- combine_OAK = Xiao_OAK %>% inner_join(Jeff_OAK[, c(4,2,3, 18:39)], by = "ID") %>% -->
<!--                 inner_join(Hauke_dat %>% select(USUBJID, ACTARM, OS_MONTHS, OS_CENSOR, PFS_MONTHS, PFS_CENSOR), by = "USUBJID")  %>%  -->
<!--                 mutate(Final.call = factor(Final.call, levels = c("Inflamed", "Excluded", "Desert"))) -->


<!-- fea = names(rf_training$trainingData)[-which(names(rf_training$trainingData) == ".outcome")] -->

<!-- names(combine_OAK)[55:74] = gsub(" ", ".", names(combine_OAK)[55:74]) -->

<!-- combine_OAK = combine_OAK[complete.cases(combine_OAK), ] -->
<!-- ``` -->


<!-- # prediction on OAK (combing arms) -->
<!-- ```{r} -->
<!-- pred <- predict(rf_training,  -->
<!--                 combine_OAK[, fea],  -->
<!--                 type = "prob") -->

<!-- xtab = table(factor(c("Desert", "Excluded", "Inflamed")[apply(pred, 1, which.max)], levels = c("Inflamed", "Excluded", "Desert")) -->
<!-- , combine_OAK$Final.call) -->

<!-- print(paste0("Classification accuracy is ", sum(diag(xtab))/sum(xtab))) -->

<!-- vcd::Kappa(xtab) -->
<!-- xtab -->

<!-- auc = pROC::multiclass.roc(response = combine_OAK$Final.call, predictor = pred[, c(3,2,1)], plot = FALSE, quiet = TRUE) -->
<!-- auc -->


<!-- pip1_3_pred_OAK = data.frame("ID" = combine_OAK$ID, "ACTARM" = combine_OAK$ACTARM,  -->
<!--                              "spat" = factor(c("Desert", "Excluded", "Inflamed")[apply(pred, 1, which.max)], levels = c("Inflamed", "Excluded", "Desert")),  -->
<!--                              "Manual" = combine_OAK$Final.call, -->
<!--                              "SVM" = combine_OAK$`SVM prediction`, -->
<!--                              "cutoff" = combine_OAK$`Cutoff prediction`) -->

<!-- ``` -->



<!-- # OS Survival analysis (OAK) -->
<!-- ```{r} -->
<!-- COLOR <- c("#ED7D31", "#4472C4", "#A5A5A5") -->

<!-- A_dat = combine_OAK %>% filter(ACTARM == "atezo") -->
<!-- D_dat = combine_OAK %>% filter(ACTARM == "doce")  -->

<!-- pred <- predict(rf_training,  -->
<!--                 A_dat[, fea],  -->
<!--                 type = "prob") -->

<!-- A_dat$spat = factor(c("Desert", "Excluded", "Inflamed")[apply(pred, 1, which.max)], levels = c("Inflamed", "Excluded", "Desert")) -->

<!-- pred <- predict(rf_training,  -->
<!--                 D_dat[, fea],  -->
<!--                 type = "prob") -->

<!-- D_dat$spat = factor(c("Desert", "Excluded", "Inflamed")[apply(pred, 1, which.max)], levels = c("Inflamed", "Excluded", "Desert")) -->

<!-- A_dat = A_dat %>% select(spat, Final.call, cutoff = `Cutoff prediction`, SVM = `SVM prediction`, OS_MONTHS, OS_CENSOR, PFS_MONTHS, PFS_CENSOR) -->

<!-- A_dat$cutoff = factor(A_dat$cutoff, levels = c("Inflamed", "Excluded", "Desert")) -->
<!-- A_dat$SVM = factor(A_dat$SVM, levels = c("Inflamed", "Excluded", "Desert")) -->


<!-- D_dat = D_dat %>% select(spat, Final.call, cutoff = `Cutoff prediction`, SVM = `SVM prediction`, OS_MONTHS, OS_CENSOR, PFS_MONTHS, PFS_CENSOR) -->

<!-- D_dat$cutoff = factor(D_dat$cutoff, levels = c("Inflamed", "Excluded", "Desert")) -->
<!-- D_dat$SVM = factor(D_dat$SVM, levels = c("Inflamed", "Excluded", "Desert")) -->

<!-- ``` -->


<!-- ```{r} -->
<!-- ####################################################################################################### -->
<!-- ########################        OS for cut-off, SVM, MOCHA and Manuals       ######################## -->
<!-- ####################################################################################################### -->

<!-- ## Atezo arm -->

<!-- fit_spat <- survfit(Surv(OS_MONTHS, OS_CENSOR) ~ spat, data = A_dat) -->
<!-- fit_manual <- survfit(Surv(OS_MONTHS, OS_CENSOR) ~ Final.call, data = A_dat) -->
<!-- fit_cutoff <- survfit(Surv(OS_MONTHS, OS_CENSOR) ~ cutoff, data = A_dat) -->
<!-- fit_SVM <- survfit(Surv(OS_MONTHS, OS_CENSOR) ~ SVM, data = A_dat) -->


<!-- p_spat_A_OS = ggsurvplot(fit_spat, data = A_dat, palette = COLOR, size = 2,  -->
<!--                          font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                          legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                          conf.int = F,          # Add confidence interval -->
<!--                          pval = FALSE,              # Add p-value -->
<!--                          risk.table = TRUE,  title = "OS for Atezolizumab by MOCHA", ggtheme=custom_theme(), -->
<!--                          surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(OS_MONTHS, OS_CENSOR) ~ spat, data = A_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_spat)[,2] -->

<!-- p_spat_A_OS$plot <- p_spat_A_OS$plot + -->
<!--   annotate("text", size = 7, x = 28, y = 0.95, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 1.8, fontface=1) -->

<!-- print(p_spat_A_OS) -->




<!-- p_manual_A_OS = ggsurvplot(fit_manual, data = A_dat, palette = COLOR, size = 2,  -->
<!--                            font.main = c(18, "bold"), legend.title = "Immunophenotyping",  -->
<!--                            legend.labs = c("Inflamed", "Excluded", "Desert"),  -->
<!--                            conf.int = F,          # Add confidence interval -->
<!--                            pval = FALSE,              # Add p-value -->
<!--                            risk.table = TRUE,  title = "OS for Atezolizumab by Manual", ggtheme=custom_theme(), -->
<!--                            surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(OS_MONTHS, OS_CENSOR) ~ Final.call, data = A_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_manual)[,2] -->

<!-- p_manual_A_OS$plot <- p_manual_A_OS$plot + -->
<!--   annotate("text", size = 7, x = 28, y = 0.95, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 1.8, fontface=1) -->

<!-- print(p_manual_A_OS) -->


<!-- p_cutoff_A_OS = ggsurvplot(fit_cutoff, data = A_dat, palette = COLOR, size = 2,  -->
<!--                            font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                            legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                            conf.int = F,          # Add confidence interval -->
<!--                            pval = FALSE,              # Add p-value -->
<!--                            risk.table = TRUE,  title = "OS for Atezolizumab by Density cut-off", ggtheme=custom_theme(), -->
<!--                            surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(OS_MONTHS, OS_CENSOR) ~ cutoff, data = A_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_cutoff)[,2] -->

<!-- p_cutoff_A_OS$plot <- p_cutoff_A_OS$plot + -->
<!--   annotate("text", size = 7, x = 28, y = 0.95, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 1.5, fontface=1) -->

<!-- print(p_cutoff_A_OS) -->





<!-- p_SVM_A_OS = ggsurvplot(fit_SVM, data = A_dat, palette = COLOR, size = 2,  -->
<!--                         font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                         legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                         conf.int = F,          # Add confidence interval -->
<!--                         pval = FALSE,              # Add p-value -->
<!--                         risk.table = TRUE,  title = "OS for Atezolizumab by Binned CD8 density", ggtheme=custom_theme(), -->
<!--                         surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(OS_MONTHS, OS_CENSOR) ~ SVM, data = A_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_spat)[,2] -->

<!-- p_SVM_A_OS$plot <- p_SVM_A_OS$plot + -->
<!--   annotate("text", size = 7, x = 28, y = 0.95, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 1.8, fontface=1) -->

<!-- print(p_SVM_A_OS) -->






<!-- ## Doce arm -->

<!-- fit_spat <- survfit(Surv(OS_MONTHS, OS_CENSOR) ~ spat, data = D_dat) -->
<!-- fit_manual <- survfit(Surv(OS_MONTHS, OS_CENSOR) ~ Final.call, data = D_dat) -->
<!-- fit_cutoff <- survfit(Surv(OS_MONTHS, OS_CENSOR) ~ cutoff, data = D_dat) -->
<!-- fit_SVM <- survfit(Surv(OS_MONTHS, OS_CENSOR) ~ SVM, data = D_dat) -->


<!-- p_spat_D_OS = ggsurvplot(fit_spat, data = D_dat, palette = COLOR, size = 2,  -->
<!--                          font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                          legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                          conf.int = F,          # Add confidence interval -->
<!--                          pval = FALSE,              # Add p-value -->
<!--                          risk.table = TRUE,  title = "OS for Docetaxel by MOCHA", ggtheme=custom_theme(), -->
<!--                          surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(OS_MONTHS, OS_CENSOR) ~ spat, data = D_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_spat)[,2] -->

<!-- p_spat_D_OS$plot <- p_spat_D_OS$plot + -->
<!--   annotate("text", size = 7, x = 28, y = 0.95, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = 0, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = -1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 1.8, fontface=1) -->

<!-- print(p_spat_D_OS) -->




<!-- p_manual_D_OS = ggsurvplot(fit_manual, data = D_dat, palette = COLOR, size = 2,  -->
<!--                            font.main = c(18, "bold"), legend.title = "Immunophenotyping",  -->
<!--                            legend.labs = c("Inflamed", "Excluded", "Desert"),  -->
<!--                            conf.int = F,          # Add confidence interval -->
<!--                            pval = FALSE,              # Add p-value -->
<!--                            risk.table = TRUE,  title = "OS for Docetaxel by Manual", ggtheme=custom_theme(), -->
<!--                            surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(OS_MONTHS, OS_CENSOR) ~ Final.call, data = D_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_manual)[,2] -->

<!-- p_manual_D_OS$plot <- p_manual_D_OS$plot + -->
<!--   annotate("text", size = 7, x = 28, y = 0.95, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = 0, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = -1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 1.8, fontface=1) -->

<!-- print(p_manual_D_OS) -->



<!-- p_cutoff_D_OS = ggsurvplot(fit_cutoff, data = D_dat, palette = COLOR, size = 2,  -->
<!--                            font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                            legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                            conf.int = F,          # Add confidence interval -->
<!--                            pval = FALSE,              # Add p-value -->
<!--                            risk.table = TRUE,  title = "OS for Docetaxel by Density cut-off", ggtheme=custom_theme(), -->
<!--                            surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(OS_MONTHS, OS_CENSOR) ~ cutoff, data = D_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_cutoff)[,2] -->

<!-- p_cutoff_D_OS$plot <- p_cutoff_D_OS$plot + -->
<!--   annotate("text", size = 7, x = 28, y = 0.95, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = 0, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = -1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 1.5, fontface=1) -->

<!-- print(p_cutoff_D_OS) -->




<!-- p_SVM_D_OS = ggsurvplot(fit_SVM, data = D_dat, palette = COLOR, size = 2,  -->
<!--                         font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                         legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                         conf.int = F,          # Add confidence interval -->
<!--                         pval = FALSE,              # Add p-value -->
<!--                         risk.table = TRUE,  title = "OS for Docetaxel by Binned CD8 density", ggtheme=custom_theme(), -->
<!--                         surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(OS_MONTHS, OS_CENSOR) ~ SVM, data = D_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_SVM)[,2] -->

<!-- p_SVM_D_OS$plot <- p_SVM_D_OS$plot + -->
<!--   annotate("text", size = 7, x = 28, y = 0.95, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 1.8, fontface=1) -->

<!-- print(p_SVM_D_OS) -->



<!-- ``` -->



<!-- # PFS Survival analysis (OAK) -->
<!-- ```{r} -->

<!-- ####################################################################################################### -->
<!-- ########################        PFS for cut-off, LATIS and Manuals       ######################## -->
<!-- ####################################################################################################### -->

<!-- ## Atezo arm -->

<!-- fit_spat <- survfit(Surv(PFS_MONTHS, PFS_CENSOR) ~ spat, data = A_dat) -->
<!-- fit_manual <- survfit(Surv(PFS_MONTHS, PFS_CENSOR) ~ Final.call, data = A_dat) -->
<!-- fit_cutoff <- survfit(Surv(PFS_MONTHS, PFS_CENSOR) ~ cutoff, data = A_dat) -->
<!-- fit_SVM <- survfit(Surv(PFS_MONTHS, PFS_CENSOR) ~ SVM, data = A_dat) -->


<!-- p_spat_A_PFS = ggsurvplot(fit_spat, data = A_dat, palette = COLOR, size = 2,  -->
<!--                           font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                           legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                           conf.int = F,          # Add confidence interval -->
<!--                           pval = FALSE,              # Add p-value -->
<!--                           risk.table = TRUE,  title = "PFS for Atezolizumab by MOCHA", ggtheme=custom_theme(), -->
<!--                           surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(PFS_MONTHS, PFS_CENSOR) ~ spat, data = A_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_spat)[,2] -->

<!-- p_spat_A_PFS$plot <- p_spat_A_PFS$plot + -->
<!--   annotate("text", size = 7, x = 28, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -2, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 1.5, fontface=1) -->

<!-- print(p_spat_A_PFS) -->




<!-- p_manual_A_PFS = ggsurvplot(fit_manual, data = A_dat, palette = COLOR, size = 2,  -->
<!--                             font.main = c(18, "bold"), legend.title = "Immunophenotyping",  -->
<!--                             legend.labs = c("Inflamed", "Excluded", "Desert"),  -->
<!--                             conf.int = F,          # Add confidence interval -->
<!--                             pval = FALSE,              # Add p-value -->
<!--                             risk.table = TRUE,  title = "PFS for Atezolizumab by Manual", ggtheme=custom_theme(), -->
<!--                             surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(PFS_MONTHS, PFS_CENSOR) ~ Final.call, data = A_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_manual)[,2] -->

<!-- p_manual_A_PFS$plot <- p_manual_A_PFS$plot + -->
<!--   annotate("text", size = 7, x = 28, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -2, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 1.5, fontface=1) -->

<!-- print(p_manual_A_PFS) -->




<!-- p_cutoff_A_PFS = ggsurvplot(fit_cutoff, data = A_dat, palette = COLOR, size = 2,  -->
<!--                             font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                             legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                             conf.int = F,          # Add confidence interval -->
<!--                             pval = FALSE,              # Add p-value -->
<!--                             risk.table = TRUE,  title = "PFS for Atezolizumab by Density cut-off", ggtheme=custom_theme(), -->
<!--                             surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(PFS_MONTHS, PFS_CENSOR) ~ cutoff, data = A_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_cutoff)[,2] -->

<!-- p_cutoff_A_PFS$plot <- p_cutoff_A_PFS$plot + -->
<!--   annotate("text", size = 7, x = 28, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -2, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 1.5, fontface=1) -->

<!-- print(p_cutoff_A_PFS) -->





<!-- p_SVM_A_PFS = ggsurvplot(fit_SVM, data = A_dat, palette = COLOR, size = 2,  -->
<!--                          font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                          legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                          conf.int = F,          # Add confidence interval -->
<!--                          pval = FALSE,              # Add p-value -->
<!--                          risk.table = TRUE,  title = "PFS for Atezolizumab by Binned CD8 density", ggtheme=custom_theme(), -->
<!--                          surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(PFS_MONTHS, PFS_CENSOR) ~ SVM, data = A_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_spat)[,2] -->

<!-- p_SVM_A_PFS$plot <- p_SVM_A_PFS$plot + -->
<!--   annotate("text", size = 7, x = 28, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -2, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 1.5, fontface=1) -->

<!-- print(p_SVM_A_PFS) -->





<!-- ## Doce arm -->

<!-- fit_spat <- survfit(Surv(PFS_MONTHS, PFS_CENSOR) ~ spat, data = D_dat) -->
<!-- fit_manual <- survfit(Surv(PFS_MONTHS, PFS_CENSOR) ~ Final.call, data = D_dat) -->
<!-- fit_cutoff <- survfit(Surv(PFS_MONTHS, PFS_CENSOR) ~ cutoff, data = D_dat) -->
<!-- fit_SVM <- survfit(Surv(PFS_MONTHS, PFS_CENSOR) ~ SVM, data = D_dat) -->


<!-- p_spat_D_PFS = ggsurvplot(fit_spat, data = D_dat, palette = COLOR, size = 2,  -->
<!--                           font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                           legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                           conf.int = F,          # Add confidence interval -->
<!--                           pval = FALSE,              # Add p-value -->
<!--                           risk.table = TRUE,  title = "PFS for Docetaxel by MOCHA", ggtheme=custom_theme(), -->
<!--                           surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(PFS_MONTHS, PFS_CENSOR) ~ spat, data = D_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_spat)[,2] -->

<!-- p_spat_D_PFS$plot <- p_spat_D_PFS$plot + -->
<!--   annotate("text", size = 7, x = 28, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -2, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 2, fontface=1) -->

<!-- print(p_spat_D_PFS) -->




<!-- p_manual_D_PFS = ggsurvplot(fit_manual, data = D_dat, palette = COLOR, size = 2,  -->
<!--                             font.main = c(18, "bold"), legend.title = "Immunophenotyping",  -->
<!--                             legend.labs = c("Inflamed", "Excluded", "Desert"),  -->
<!--                             conf.int = F,          # Add confidence interval -->
<!--                             pval = FALSE,              # Add p-value -->
<!--                             risk.table = TRUE,  title = "PFS for Docetaxel by Manual", ggtheme=custom_theme(), -->
<!--                             surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(PFS_MONTHS, PFS_CENSOR) ~ Final.call, data = D_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_manual)[,2] -->

<!-- p_manual_D_PFS$plot <- p_manual_D_PFS$plot + -->
<!--   annotate("text", size = 7, x = 28, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -2, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 2, fontface=1) -->

<!-- print(p_manual_D_PFS) -->



<!-- p_cutoff_D_PFS = ggsurvplot(fit_cutoff, data = D_dat, palette = COLOR, size = 2,  -->
<!--                             font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                             legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                             conf.int = F,          # Add confidence interval -->
<!--                             pval = FALSE,              # Add p-value -->
<!--                             risk.table = TRUE,  title = "PFS for Docetaxel by Density cut-off", ggtheme=custom_theme(), -->
<!--                             surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(PFS_MONTHS, PFS_CENSOR) ~ cutoff, data = D_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_cutoff)[,2] -->

<!-- p_cutoff_D_PFS$plot <- p_cutoff_D_PFS$plot + -->
<!--   annotate("text", size = 7, x = 28, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -2, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 2, fontface=1) -->

<!-- print(p_cutoff_D_PFS) -->




<!-- p_SVM_D_PFS = ggsurvplot(fit_SVM, data = D_dat, palette = COLOR, size = 2,  -->
<!--                          font.main = c(18, "bold"), legend.title = "Immunophenotyping",  -->
<!--                          legend.labs = c("Inflamed", "Excluded", "Desert"),  -->
<!--                          conf.int = F,          # Add confidence interval -->
<!--                          pval = FALSE,              # Add p-value -->
<!--                          risk.table = TRUE,  title = "PFS for Docetaxel by Binned CD8 density", ggtheme=custom_theme(), -->
<!--                          surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(PFS_MONTHS, PFS_CENSOR) ~ SVM, data = D_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_SVM)[,2] -->

<!-- p_SVM_D_PFS$plot <- p_SVM_D_PFS$plot + -->
<!--   annotate("text", size = 7, x = 28, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.8, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -2, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.8, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.8, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 2, fontface=1) -->

<!-- print(p_SVM_D_PFS) -->




<!-- ``` -->


<!-- ```{r} -->

<!-- splots <- list() -->
<!-- splots[[1]] <- p_cutoff_A_OS -->
<!-- splots[[2]] <- p_SVM_A_OS -->
<!-- splots[[3]] <- p_spat_A_OS -->
<!-- splots[[4]] <- p_manual_A_OS -->
<!-- splots[[5]] <- p_cutoff_D_OS -->
<!-- splots[[6]] <- p_SVM_D_OS -->
<!-- splots[[7]] <- p_spat_D_OS -->
<!-- splots[[8]] <- p_manual_D_OS -->



<!-- splots[[9]] <- p_cutoff_A_PFS -->
<!-- splots[[10]] <- p_SVM_A_PFS -->
<!-- splots[[11]] <- p_spat_A_PFS -->
<!-- splots[[12]] <- p_manual_A_PFS -->
<!-- splots[[13]] <- p_cutoff_D_PFS -->
<!-- splots[[14]] <- p_SVM_D_PFS -->
<!-- splots[[15]] <- p_spat_D_PFS -->
<!-- splots[[16]] <- p_manual_D_PFS -->



<!-- png("OS_comp_new_preferred_OAK_pip1-3.png", width = 7300, height = 3800, res = 300) -->
<!-- # Arrange multiple ggsurvplots and print the output -->
<!-- arrange_ggsurvplots(list(splots[[1]], splots[[5]], splots[[2]], splots[[6]], -->
<!--                          splots[[3]], splots[[7]], splots[[4]], splots[[8]]),  -->
<!--                     print = TRUE, ncol = 4, nrow = 2, risk.table.height = 0.2) -->
<!-- dev.off() -->


<!-- png("PFS_comp_new_preferred_OAK_pip1-3.png", width = 7300, height = 3800, res = 300) -->
<!-- # Arrange multiple ggsurvplots and print the output -->
<!-- arrange_ggsurvplots(list(splots[[9]], splots[[13]], splots[[10]], splots[[14]], -->
<!--                          splots[[11]], splots[[15]], splots[[12]], splots[[16]]),  -->
<!--                     print = TRUE, ncol = 4, nrow = 2, risk.table.height = 0.2) -->
<!-- dev.off() -->


<!-- ``` -->






<!-- # prediction on IMPassion130 (combing arms) -->
<!-- ```{r, warning=FALSE} -->
<!-- Jeff_IMP130 = readxl::read_xlsx('20221002_IMP130_tracker.xlsx', sheet = 1, col_types = c(rep("text", 12), rep("numeric", 27))) %>% mutate(Final.call = factor(Immunophenotype_HK, levels = c("Inflamed", "Excluded", "Desert"))) -->
<!-- Jeff_IMP130 = Jeff_IMP130[-c(1:8, 10, 11, 14, 16, 17), ] -->
<!-- Jeff_IMP130$ID = paste0(Jeff_IMP130$Block, '_', as.numeric(Jeff_IMP130$`Patient Number`), '_ckpos_tiles.csv') -->
<!-- Jeff_IMP130 = Jeff_IMP130[, c(21:29, 31:39, 40, 41)]; names(Jeff_IMP130)[1:18] = gsub(" ", ".", names(Jeff_IMP130)[1:18]) -->

<!-- Xiao_IMP130 = read.csv('IMPassion130_res.csv'); Xiao_IMP130 = Xiao_IMP130[, -which(colnames(Xiao_IMP130) == "ID.1")[1]] -->

<!-- # Jeff_IMP130$ID[!(Jeff_IMP130$ID %in% Xiao_IMP130$ID)]  -->
<!-- # "HP-208267_1175_ckpos_tiles.csv" "HP-208290_1209_ckpos_tiles.csv" "HP-208637_1517_ckpos_tiles.csv"  -->
<!-- # these 3 files are either short of pos tiles or neg tiles -->

<!-- combine_IMP130 = merge(Jeff_IMP130, Xiao_IMP130, by = "ID") -->
<!-- combine_IMP130 = combine_IMP130[complete.cases(combine_IMP130),] -->

<!-- pred <- predict(rf_training,  -->
<!--                 combine_IMP130[, fea],  -->
<!--                 type = "prob") -->

<!-- xtab = table(factor(c("Desert", "Excluded", "Inflamed")[apply(pred, 1, which.max)], levels = c("Inflamed", "Excluded", "Desert")) -->
<!-- , combine_IMP130$Final.call) -->

<!-- print(paste0("Classification accuracy is ", sum(diag(xtab))/sum(xtab))) -->

<!-- vcd::Kappa(xtab) -->
<!-- xtab -->

<!-- auc = pROC::multiclass.roc(response = combine_IMP130$Final.call, predictor = pred[, c(3, 2, 1)], plot = FALSE, quiet = TRUE) -->
<!-- auc -->
<!-- ``` -->


<!-- ```{r} -->

<!-- tmp1 = read.csv('20221130_IMP130_tracker_ANON.csv') %>% select(uni_id = hashed.uniId, HK_block = 'Specimen.._HK',  -->
<!--                                                                SVM = SVM_prediction, cutoff = Slide_Cutoff_prediction) -->
<!-- tmp2 = read.csv('wo29522_clin_jea_hk_10022022.csv') -->

<!-- tmp3 = merge(tmp1, tmp2, by = "uni_id") -->

<!-- combine_IMP130 = combine_IMP130 %>% mutate(HK_block = substr(ID, 1, 9), -->
<!--                                      spat = factor(c("Desert", "Excluded", "Inflamed")[apply(pred, 1, which.max)], levels = c("Inflamed", "Excluded", "Desert"))) %>% select(HK_block, Final.call, spat) -->

<!-- dat_IMP130 = merge(combine_IMP130,  -->
<!--                    tmp3 %>% select(HK_block, SVM, cutoff, os_months, os_cnsr, pfs_months, pfs_cnsr, arm),  -->
<!--                    by = "HK_block") -->

<!-- dat_IMP130$SVM = factor(dat_IMP130$SVM, levels = c("Inflamed", "Excluded", "Desert")) -->
<!-- dat_IMP130$cutoff = factor(dat_IMP130$cutoff, levels = c("Inflamed", "Excluded", "Desert")) -->

<!-- pip1_3_pred_IMP130 = dat_IMP130 %>% select("ID" = HK_block, "Manual" = Final.call, "spat" = spat,  -->
<!--                                            "SVM" = SVM, -->
<!--                                            "cutoff" = cutoff, -->
<!--                                            "ACTARM" = arm)   -->
<!-- ``` -->


<!-- # OS Survival analysis (IMPassion130) -->
<!-- ```{r} -->
<!-- COLOR <- c("#ED7D31", "#4472C4", "#A5A5A5") -->

<!-- A_dat = dat_IMP130 %>% filter(arm == "MPDL3280A") -->

<!-- D_dat = dat_IMP130 %>% filter(arm == "PLACEBO") -->
<!-- ####################################################################################################### -->
<!-- ########################            OS for spat and Manuals         ######################## -->
<!-- ####################################################################################################### -->

<!-- ## Atezo arm -->
<!-- fit_spat <- survfit(Surv(os_months, 1-os_cnsr) ~ spat, data = A_dat) -->
<!-- fit_manual <- survfit(Surv(os_months, 1-os_cnsr) ~ Final.call, data = A_dat) -->
<!-- fit_cutoff <- survfit(Surv(os_months, 1-os_cnsr) ~ cutoff, data = A_dat) -->
<!-- fit_SVM <- survfit(Surv(os_months, 1-os_cnsr) ~ SVM, data = A_dat) -->


<!-- p_spat_A_OS = ggsurvplot(fit_spat, data = A_dat, palette = COLOR, size = 2,  -->
<!--                          font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                          legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                          conf.int = F,          # Add confidence interval -->
<!--                          pval = FALSE,              # Add p-value -->
<!--                          risk.table = TRUE,  title = "OS for Atezolizumab by MOCHA", ggtheme=custom_theme(), -->
<!--                          surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(os_months, 1-os_cnsr) ~ spat, data = A_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_spat)[,2] -->

<!-- p_spat_A_OS$plot <- p_spat_A_OS$plot + -->
<!--   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.65, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.65, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.65, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 3, fontface=1) -->

<!-- print(p_spat_A_OS) -->



<!-- p_manual_A_OS = ggsurvplot(fit_manual, data = A_dat, palette = COLOR, size = 2,  -->
<!--                            font.main = c(18, "bold"), legend.title = "Immunophenotyping",  -->
<!--                            legend.labs = c("Inflamed", "Excluded", "Desert"),  -->
<!--                            conf.int = F,          # Add confidence interval -->
<!--                            pval = FALSE,              # Add p-value -->
<!--                            risk.table = TRUE,  title = "OS for Atezolizumab by Manual", ggtheme=custom_theme(), -->
<!--                            surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(os_months, 1-os_cnsr) ~ Final.call, data = A_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_manual)[,2] -->

<!-- p_manual_A_OS$plot <- p_manual_A_OS$plot + -->
<!--   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.65, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.65, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.65, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 3, fontface=1) -->

<!-- print(p_manual_A_OS) -->


<!-- p_cutoff_A_OS = ggsurvplot(fit_cutoff, data = A_dat, palette = COLOR, size = 2,  -->
<!--                            font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                            legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                            conf.int = F,          # Add confidence interval -->
<!--                            pval = FALSE,              # Add p-value -->
<!--                            risk.table = TRUE,  title = "OS for Atezolizumab by Density cut-off", ggtheme=custom_theme(), -->
<!--                            surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(os_months, 1-os_cnsr) ~ cutoff, data = A_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_cutoff)[,2] -->

<!-- p_cutoff_A_OS$plot <- p_cutoff_A_OS$plot + -->
<!--   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.65, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.65, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.65, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 3, fontface=1) -->

<!-- print(p_cutoff_A_OS) -->



<!-- p_SVM_A_OS = ggsurvplot(fit_SVM, data = A_dat, palette = COLOR, size = 2,  -->
<!--                         font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                         legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                         conf.int = F,          # Add confidence interval -->
<!--                         pval = FALSE,              # Add p-value -->
<!--                         risk.table = TRUE,  title = "OS for Atezolizumab by Binned CD8 density", ggtheme=custom_theme(), -->
<!--                         surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(os_months, 1-os_cnsr) ~ SVM, data = A_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_SVM)[,2] -->

<!-- p_SVM_A_OS$plot <- p_SVM_A_OS$plot + -->
<!--   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.65, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.65, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.65, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 3, fontface=1) -->

<!-- print(p_SVM_A_OS) -->




<!-- ## Placebo arm -->
<!-- fit_spat <- survfit(Surv(os_months, 1-os_cnsr) ~ spat, data = D_dat) -->
<!-- fit_manual <- survfit(Surv(os_months, 1-os_cnsr) ~ Final.call, data = D_dat) -->
<!-- fit_cutoff <- survfit(Surv(os_months, 1-os_cnsr) ~ cutoff, data = D_dat) -->
<!-- fit_SVM <- survfit(Surv(os_months, 1-os_cnsr) ~ SVM, data = D_dat) -->


<!-- p_spat_D_OS = ggsurvplot(fit_spat, data = D_dat, palette = COLOR, size = 2,  -->
<!--                          font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                          legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                          conf.int = F,          # Add confidence interval -->
<!--                          pval = FALSE,              # Add p-value -->
<!--                          risk.table = TRUE,  title = "OS for Placebo by MOCHA", ggtheme=custom_theme(), -->
<!--                          surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(os_months, 1-os_cnsr) ~ spat, data = D_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_spat)[,2] -->

<!-- p_spat_D_OS$plot <- p_spat_D_OS$plot + -->
<!--   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.65, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = 3, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.65, label = round(med_time[2], 1), cex=7, col=COLOR[3], vjust=0, hjust = -1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.65, label = round(med_time[3], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0.5, fontface=1) -->

<!-- print(p_spat_D_OS) -->



<!-- p_manual_D_OS = ggsurvplot(fit_manual, data = D_dat, palette = COLOR, size = 2,  -->
<!--                            font.main = c(18, "bold"), legend.title = "Immunophenotyping",  -->
<!--                            legend.labs = c("Inflamed", "Excluded", "Desert"),  -->
<!--                            conf.int = F,          # Add confidence interval -->
<!--                            pval = FALSE,              # Add p-value -->
<!--                            risk.table = TRUE,  title = "OS for Placebo by Manual", ggtheme=custom_theme(), -->
<!--                            surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(os_months, 1-os_cnsr) ~ Final.call, data = D_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_manual)[,2] -->

<!-- p_manual_D_OS$plot <- p_manual_D_OS$plot + -->
<!--   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.65, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = 3, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.65, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.65, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = -1, fontface=1) -->

<!-- print(p_manual_D_OS) -->



<!-- p_cutoff_D_OS = ggsurvplot(fit_cutoff, data = D_dat, palette = COLOR, size = 2,  -->
<!--                            font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                            legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                            conf.int = F,          # Add confidence interval -->
<!--                            pval = FALSE,              # Add p-value -->
<!--                            risk.table = TRUE,  title = "OS for Placebo by Density cut-off", ggtheme=custom_theme(), -->
<!--                            surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(os_months, 1-os_cnsr) ~ cutoff, data = D_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_cutoff)[,2] -->

<!-- p_cutoff_D_OS$plot <- p_cutoff_D_OS$plot + -->
<!--   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.65, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = 3, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.65, label = round(med_time[2], 1), cex=7, col=COLOR[3], vjust=0, hjust = -1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.65, label = round(med_time[3], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0.5, fontface=1) -->

<!-- print(p_cutoff_D_OS) -->



<!-- p_SVM_D_OS = ggsurvplot(fit_SVM, data = D_dat, palette = COLOR, size = 2,  -->
<!--                         font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                         legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                         conf.int = F,          # Add confidence interval -->
<!--                         pval = FALSE,              # Add p-value -->
<!--                         risk.table = TRUE,  title = "OS for Placebo by Binned CD8 density", ggtheme=custom_theme(), -->
<!--                         surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(os_months, 1-os_cnsr) ~ SVM, data = D_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_SVM)[,2] -->

<!-- p_SVM_D_OS$plot <- p_SVM_D_OS$plot + -->
<!--   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.65, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = 3, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.65, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = 0.5, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.65, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = -1, fontface=1) -->

<!-- print(p_SVM_D_OS) -->


<!-- ``` -->




<!-- # PFS Survival analysis (IMPassion130) -->
<!-- ```{r} -->

<!-- ####################################################################################################### -->
<!-- ########################            PFS for spat and Manuals         ######################## -->
<!-- ####################################################################################################### -->

<!-- ## Atezo arm -->
<!-- fit_spat <- survfit(Surv(pfs_months, 1-pfs_cnsr) ~ spat, data = A_dat) -->
<!-- fit_manual <- survfit(Surv(pfs_months, 1-pfs_cnsr) ~ Final.call, data = A_dat) -->
<!-- fit_cutoff <- survfit(Surv(pfs_months, 1-pfs_cnsr) ~ cutoff, data = A_dat) -->
<!-- fit_SVM <- survfit(Surv(pfs_months, 1-pfs_cnsr) ~ SVM, data = A_dat) -->


<!-- p_spat_A_pfs = ggsurvplot(fit_spat, data = A_dat, palette = COLOR, size = 2,  -->
<!--                           font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                           legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                           conf.int = F,          # Add confidence interval -->
<!--                           pval = FALSE,              # Add p-value -->
<!--                           risk.table = TRUE,  title = "PFS for Atezolizumab by MOCHA", ggtheme=custom_theme(), -->
<!--                           surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(pfs_months, 1-pfs_cnsr) ~ spat, data = A_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_spat)[,2] -->

<!-- p_spat_A_pfs$plot <- p_spat_A_pfs$plot + -->
<!--   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.65, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -1.5, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.65, label = round(med_time[2], 1), cex=7, col=COLOR[3], vjust=0, hjust = 2, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.65, label = round(med_time[3], 1), cex=7, col=COLOR[2], vjust=0, hjust = -0.5, fontface=1) -->

<!-- print(p_spat_A_pfs) -->



<!-- p_manual_A_pfs = ggsurvplot(fit_manual, data = A_dat, palette = COLOR, size = 2,  -->
<!--                             font.main = c(18, "bold"), legend.title = "Immunophenotyping",  -->
<!--                             legend.labs = c("Inflamed", "Excluded", "Desert"),  -->
<!--                             conf.int = F,          # Add confidence interval -->
<!--                             pval = FALSE,              # Add p-value -->
<!--                             risk.table = TRUE,  title = "PFS for Atezolizumab by Manual", ggtheme=custom_theme(), -->
<!--                             surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(pfs_months, 1-pfs_cnsr) ~ Final.call, data = A_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_manual)[,2] -->

<!-- p_manual_A_pfs$plot <- p_manual_A_pfs$plot + -->
<!--   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.65, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -1.5, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.65, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = -0.5, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.65, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 2, fontface=1) -->

<!-- print(p_manual_A_pfs) -->


<!-- p_cutoff_A_pfs = ggsurvplot(fit_cutoff, data = A_dat, palette = COLOR, size = 2,  -->
<!--                             font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                             legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                             conf.int = F,          # Add confidence interval -->
<!--                             pval = FALSE,              # Add p-value -->
<!--                             risk.table = TRUE,  title = "PFS for Atezolizumab by Density cut-off", ggtheme=custom_theme(), -->
<!--                             surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(pfs_months, 1-pfs_cnsr) ~ cutoff, data = A_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_cutoff)[,2] -->

<!-- p_cutoff_A_pfs$plot <- p_cutoff_A_pfs$plot + -->
<!--   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.65, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -1.5, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.65, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = -0.5, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.65, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 2, fontface=1) -->

<!-- print(p_cutoff_A_pfs) -->



<!-- p_SVM_A_pfs = ggsurvplot(fit_SVM, data = A_dat, palette = COLOR, size = 2,  -->
<!--                          font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                          legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                          conf.int = F,          # Add confidence interval -->
<!--                          pval = FALSE,              # Add p-value -->
<!--                          risk.table = TRUE,  title = "PFS for Atezolizumab by Binned CD8 density", ggtheme=custom_theme(), -->
<!--                          surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(pfs_months, 1-pfs_cnsr) ~ SVM, data = A_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_SVM)[,2] -->

<!-- p_SVM_A_pfs$plot <- p_SVM_A_pfs$plot + -->
<!--   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.65, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = -1.5, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.65, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = -0.5, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.65, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = 2, fontface=1) -->

<!-- print(p_SVM_A_pfs) -->






<!-- ## Placebo arm -->
<!-- fit_spat <- survfit(Surv(pfs_months, 1-pfs_cnsr) ~ spat, data = D_dat) -->
<!-- fit_manual <- survfit(Surv(pfs_months, 1-pfs_cnsr) ~ Final.call, data = D_dat) -->
<!-- fit_cutoff <- survfit(Surv(pfs_months, 1-pfs_cnsr) ~ cutoff, data = D_dat) -->
<!-- fit_SVM <- survfit(Surv(pfs_months, 1-pfs_cnsr) ~ SVM, data = D_dat) -->




<!-- p_spat_D_pfs = ggsurvplot(fit_spat, data = D_dat, palette = COLOR, size = 2,  -->
<!--                           font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                           legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                           conf.int = F,          # Add confidence interval -->
<!--                           pval = FALSE,              # Add p-value -->
<!--                           risk.table = TRUE,  title = "PFS for Placebo by MOCHA", ggtheme=custom_theme(), -->
<!--                           surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(pfs_months, 1-pfs_cnsr) ~ spat, data = D_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_spat)[,2] -->

<!-- p_spat_D_pfs$plot <- p_spat_D_pfs$plot + -->
<!--   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.65, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = 2, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.65, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = -0.5, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.65, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = -2, fontface=1) -->

<!-- print(p_spat_D_pfs) -->



<!-- p_manual_D_pfs = ggsurvplot(fit_manual, data = D_dat, palette = COLOR, size = 2,  -->
<!--                             font.main = c(18, "bold"), legend.title = "Immunophenotyping",  -->
<!--                             legend.labs = c("Inflamed", "Excluded", "Desert"),  -->
<!--                             conf.int = F,          # Add confidence interval -->
<!--                             pval = FALSE,              # Add p-value -->
<!--                             risk.table = TRUE,  title = "PFS for Placebo by Manual", ggtheme=custom_theme(), -->
<!--                             surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(pfs_months, 1-pfs_cnsr) ~ Final.call, data = D_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_manual)[,2] -->

<!-- p_manual_D_pfs$plot <- p_manual_D_pfs$plot + -->
<!--   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.65, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = 2, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.65, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = -0.5, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.65, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = -2, fontface=1) -->

<!-- print(p_manual_D_pfs) -->


<!-- p_cutoff_D_pfs = ggsurvplot(fit_cutoff, data = D_dat, palette = COLOR, size = 2,  -->
<!--                             font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                             legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                             conf.int = F,          # Add confidence interval -->
<!--                             pval = FALSE,              # Add p-value -->
<!--                             risk.table = TRUE,  title = "PFS for Placebo by Density cut-off", ggtheme=custom_theme(), -->
<!--                             surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(pfs_months, 1-pfs_cnsr) ~ cutoff, data = D_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_cutoff)[,2] -->

<!-- p_cutoff_D_pfs$plot <- p_cutoff_D_pfs$plot + -->
<!--   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.65, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = 2, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.65, label = round(med_time[2], 1), cex=7, col=COLOR[3], vjust=0, hjust = -2, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.65, label = round(med_time[3], 1), cex=7, col=COLOR[2], vjust=0, hjust = -0.5, fontface=1) -->

<!-- print(p_cutoff_D_pfs) -->



<!-- p_SVM_D_pfs = ggsurvplot(fit_SVM, data = D_dat, palette = COLOR, size = 2,  -->
<!--                          font.main = c(18, "bold"), legend.title = "Immunophenotyping", -->
<!--                          legend.labs = c("Inflamed", "Excluded", "Desert"), -->
<!--                          conf.int = F,          # Add confidence interval -->
<!--                          pval = FALSE,              # Add p-value -->
<!--                          risk.table = TRUE,  title = "PFS for Placebo by Binned CD8 density", ggtheme=custom_theme(), -->
<!--                          surv.median.line = "hv", tables.theme = theme_cleantable(), axes.offset = F, xlim = c(0, ceiling(max(A_dat$OS_MONTHS)))) -->

<!-- p_val = survdiff(Surv(pfs_months, 1-pfs_cnsr) ~ SVM, data = D_dat) -->
<!-- p_val = round(pchisq(q = p_val$chisq, df = 2, lower.tail = F), 5) -->

<!-- med_time = surv_median(fit_SVM)[,2] -->

<!-- p_SVM_D_pfs$plot <- p_SVM_D_pfs$plot + -->
<!--   annotate("text", size = 7, x = 40, y = 0.8, label = paste0("p=", p_val), cex=7, col="black", vjust=0, hjust = 1.1, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[1], y = 0.65, label = round(med_time[1], 1), cex=7, col=COLOR[1], vjust=0, hjust = 2, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[2], y = 0.65, label = round(med_time[2], 1), cex=7, col=COLOR[2], vjust=0, hjust = -0.5, fontface=1) +  -->
<!--   annotate("text", size = 7, x = med_time[3], y = 0.65, label = round(med_time[3], 1), cex=7, col=COLOR[3], vjust=0, hjust = -2, fontface=1) -->

<!-- print(p_SVM_D_pfs) -->


<!-- ``` -->


<!-- ```{r} -->

<!-- splots <- list() -->
<!-- splots[[1]] <- p_cutoff_A_OS -->
<!-- splots[[2]] <- p_SVM_A_OS -->
<!-- splots[[3]] <- p_spat_A_OS -->
<!-- splots[[4]] <- p_manual_A_OS -->
<!-- splots[[5]] <- p_cutoff_D_OS -->
<!-- splots[[6]] <- p_SVM_D_OS -->
<!-- splots[[7]] <- p_spat_D_OS -->
<!-- splots[[8]] <- p_manual_D_OS -->



<!-- splots[[9]] <- p_cutoff_A_pfs -->
<!-- splots[[10]] <- p_SVM_A_pfs -->
<!-- splots[[11]] <- p_spat_A_pfs -->
<!-- splots[[12]] <- p_manual_A_pfs -->
<!-- splots[[13]] <- p_cutoff_D_pfs -->
<!-- splots[[14]] <- p_SVM_D_pfs -->
<!-- splots[[15]] <- p_spat_D_pfs -->
<!-- splots[[16]] <- p_manual_D_pfs -->



<!-- png("OS_comp_new_preferred_IMP130_pip1-3.png", width = 7300, height = 3800, res = 300) -->
<!-- # Arrange multiple ggsurvplots and print the output -->
<!-- arrange_ggsurvplots(list(splots[[1]], splots[[5]], splots[[2]], splots[[6]], -->
<!--                          splots[[3]], splots[[7]], splots[[4]], splots[[8]]),  -->
<!--                     print = TRUE, ncol = 4, nrow = 2, risk.table.height = 0.2) -->
<!-- dev.off() -->


<!-- png("PFS_comp_new_preferred_IMP130_pip1-3.png", width = 7300, height = 3800, res = 300) -->
<!-- # Arrange multiple ggsurvplots and print the output -->
<!-- arrange_ggsurvplots(list(splots[[9]], splots[[13]], splots[[10]], splots[[14]], -->
<!--                          splots[[11]], splots[[15]], splots[[12]], splots[[16]]),  -->
<!--                     print = TRUE, ncol = 4, nrow = 2, risk.table.height = 0.2) -->
<!-- dev.off() -->


<!-- ``` -->


<!-- ```{r} -->
<!-- ## row numbers are the same for 1-3 and 4 -->
<!-- pip1_4_pred_OAK = cbind(pip1_3_pred_OAK %>% select(ID, spat, SVM, cutoff), pip4_pred_OAK) -->

<!-- pip1_4_pred_IMP130 = cbind(pip1_3_pred_IMP130 %>% select(ID, spat, SVM, cutoff), pip4_pred_IMP130) -->

<!-- if (!file.exists('~/Automated_Immunophenotyping/pip1_4_pred_OAK.csv')){ -->
<!--   write.csv(pip1_4_pred_OAK, '~/Automated_Immunophenotyping/pip1_4_pred_OAK.csv', row.names = F) -->
<!-- } -->


<!-- if (!file.exists('~/Automated_Immunophenotyping/pip1_4_pred_IMP130.csv')){ -->
<!--   write.csv(pip1_4_pred_IMP130, '~/Automated_Immunophenotyping/pip1_4_pred_IMP130.csv', row.names = F) -->
<!-- } -->


<!-- ``` -->



<!-- ```{r} -->
<!-- # UMAP for figures 3 -->
<!-- rm(list = ls()) -->

<!-- library('uwot') -->
<!-- library('dplyr') -->
<!-- select <- dplyr::select -->
<!-- library('ggplot2') -->
<!-- library('survival') -->
<!-- library("survminer") -->
<!-- library('openxlsx') -->
<!-- library('caret') -->
<!-- library('tidyverse') -->
<!-- library('rpart') -->
<!-- library('rpart.plot') -->
<!-- library('randomForest') -->
<!-- library('e1071') -->
<!-- library('openxlsx') -->
<!-- library('pROC') -->

<!-- custom_theme <- function() { -->
<!--   theme_survminer() %+replace% -->
<!--     theme( -->
<!--       plot.title=element_text(hjust=0.5) -->
<!--     ) -->
<!-- } -->


<!-- set.seed(4242) -->

<!-- library("umap") # umap_0.2.9.0 -->
<!-- COLOR <- c("#ED7D31", "#4472C4", "#A5A5A5") -->


<!-- ## POPLAR  -->
<!-- load("~/Automated_Immunophenotyping/HK_POPLAR_alltiles_100_cutoff=0.25.RData") -->
<!-- comb_res = comb_res[, -which(colnames(comb_res) == "ID")[1]] -->

<!-- POP_manual = read.csv('POPLAR_with_BCOR.csv')[, c("ID", "immunophenotype")] -->

<!-- Xiao_dat = merge(comb_res, POP_manual, by = "ID") -->

<!-- Xiao_dat = Xiao_dat[!is.na(Xiao_dat$immunophenotype),] -->


<!-- Jeff_POP = read.xlsx('20220211_poplar_bins.xlsx', sheet = 2) -->
<!-- Jeff_POP$ID = paste0(Jeff_POP$Sample.ID, '_', Jeff_POP$StarLiMS.ID, '_ckpos_tiles.csv') -->
<!-- Jeff_POP = Jeff_POP[, c(35, 8, 16:24, 26:34, 12)] -->

<!-- combine_POP = Jeff_POP %>% inner_join(Xiao_dat %>% select(-"immunophenotype"), by = "ID") %>% select(-"ID") %>%  -->
<!--                 rename("CD8_density" = "CD8.+.CK.area./.CK.area.*.100") -->




<!-- ## OAK  -->
<!-- load("~/Automated_Immunophenotyping/HK_OAK_alltiles_100_cutoff=0.25.RData") -->
<!-- Xiao_OAK = comb_res[, -which(colnames(comb_res) == "ID")[1]] -->

<!-- Jeff_OAK = readxl::read_excel('COLLATE_OAK_HK_final_20220606153656.xlsx', sheet = 1, col_types = c(rep("text", 10), rep("numeric", 27))) %>% mutate(Final.call = `Final consensus manual phenotype`) -->

<!-- Jeff_OAK$ID = paste0(Jeff_OAK$Sample.ID, '_', Jeff_OAK$StarLiMS.ID, '_ckpos_tiles.csv') -->

<!-- Hauke_dat = read.csv('Patient-MetaData_GO28915_OAK_v070_2112120_for-Darya - PatientDataTable_GO28915_OAK_new_210828.csv') -->

<!-- combine_OAK = Xiao_OAK %>% inner_join(Jeff_OAK[, c(4, 14, 2,3, 18:39)], by = "ID") %>% -->
<!--   inner_join(Hauke_dat %>% select(USUBJID, ACTARM, OS_MONTHS, OS_CENSOR, PFS_MONTHS, PFS_CENSOR), by = "USUBJID")  %>%  -->
<!--   mutate(Final.call = factor(Final.call, levels = c("Inflamed", "Excluded", "Desert"))) %>% -->
<!--   rename("CD8_density" = "CD8 + CK area / CK area * 100") -->

<!-- names(combine_OAK)[56:75] = gsub(" ", ".", names(combine_OAK)[56:75]) -->

<!-- combine_OAK = combine_OAK[complete.cases(combine_OAK), ] %>%  -->
<!--                 select(-c("ID", "USUBJID", "Cutoff prediction","SVM prediction",  -->
<!--                           "ACTARM", "OS_MONTHS", "OS_CENSOR","PFS_MONTHS", "PFS_CENSOR")) %>%  -->
<!--                 rename("Manual_Immunophenotype" = "Final.call" ) -->

<!-- combine_OAK = combine_OAK[, names(combine_OAK) %in% names(combine_POP)] -->



<!-- ## IMPassion130 -->
<!-- Jeff_IMP130 = readxl::read_xlsx('20221002_IMP130_tracker.xlsx', sheet = 1, col_types = c(rep("text", 12), rep("numeric", 27))) %>%     mutate(Final.call = factor(Immunophenotype_HK, levels = c("Inflamed", "Excluded", "Desert"))) %>%  -->
<!--   rename("CD8_density" = "CD8 + CK area / CK area * 100") -->
<!-- Jeff_IMP130 = Jeff_IMP130[-c(1:8, 10, 11, 14, 16, 17), ] -->
<!-- Jeff_IMP130$ID = paste0(Jeff_IMP130$Block, '_', as.numeric(Jeff_IMP130$`Patient Number`), '_ckpos_tiles.csv') -->
<!-- Jeff_IMP130 = Jeff_IMP130[, c(21:29, 31:39, 40, 41, 16)]; names(Jeff_IMP130)[1:18] = gsub(" ", ".", names(Jeff_IMP130)[1:18]) -->

<!-- Xiao_IMP130 = read.csv('IMPassion130_res.csv'); Xiao_IMP130 = Xiao_IMP130[, -which(colnames(Xiao_IMP130) == "ID.1")[1]] -->

<!-- combine_IMP130 = merge(Jeff_IMP130, Xiao_IMP130, by = "ID") %>%  -->
<!--                 rename("Manual_Immunophenotype" = "Final.call" ) -->
<!-- combine_IMP130 = combine_IMP130[complete.cases(combine_IMP130),] -->

<!-- combine_IMP130 = combine_IMP130[, names(combine_IMP130) %in% names(combine_POP)] -->

<!-- ``` -->



<!-- ```{r} -->
<!-- binned_density_fea <- names(combine_POP)[2:19] -->
<!-- spat_fea <- names(combine_POP)[21:70] -->
<!-- comb_fea <- c(binned_density_fea, spat_fea) -->

<!-- umap_plot <- function(this_dat = combine_POP, fea = binned_density_fea){ -->

<!--   this_dat$Immunophenotype = factor(this_dat$Manual_Immunophenotype, levels = c("Inflamed", "Excluded", "Desert")) -->


<!--   umap_fit <- this_dat %>%  -->
<!--                 select(fea) %>%  -->
<!--                 scale() %>% -->
<!--                 umap() -->


<!--   umap_df <- umap_fit$layout %>% -->
<!--                 as.data.frame() %>% -->
<!--                 rename(UMAP1 = "V1", -->
<!--                        UMAP2 = "V2") %>% -->
<!--                 mutate(ID = row_number())%>% -->
<!--                 inner_join(this_dat %>% mutate(ID = row_number()), by="ID") -->


<!--   this_fig <- ggplot(umap_df) + -->
<!--                 geom_point(aes(x = UMAP1, y = UMAP2, color = Immunophenotype)) + -->
<!--                 scale_color_manual(values = COLOR) + -->
<!--                 labs(x = "UMAP-X", -->
<!--                      y = "UMAP-Y") + -->
<!--                 theme(panel.grid.major = element_blank(),  -->
<!--                       panel.grid.minor = element_blank(), -->
<!--                       panel.background = element_blank(),  -->
<!--                       axis.line = element_line(colour = "black")) + -->
<!--                 theme(legend.position="top") -->



<!--   return(this_fig) -->

<!-- } -->


<!-- hist_plot <-  function(this_dat = combine_POP) { -->

<!--   this_dat$Immunophenotype = factor(this_dat$Manual_Immunophenotype, levels = c("Inflamed", "Excluded", "Desert")) -->
<!--   this_dat$CD8_density = log(this_dat$CD8_density) -->

<!--   this_fig = ggplot(this_dat) + -->
<!--     geom_density(aes(x = CD8_density, fill = Immunophenotype), -->
<!--                    alpha = 0.75) + -->
<!--     scale_fill_manual(values = c("Inflamed" = COLOR[1], -->
<!--                                  "Excluded" = COLOR[2], -->
<!--                                  "Desert" = COLOR[3])) + -->
<!--     labs(x = "CD8 density(log scale)", -->
<!--          y = "Smoothed counts") +  -->
<!--     xlim(-10, 5) +  -->
<!--     theme(panel.grid.major = element_blank(),  -->
<!--           panel.grid.minor = element_blank(), -->
<!--           panel.background = element_blank(),  -->
<!--           axis.line = element_line(colour = "black")) + -->
<!--     theme(legend.position="top") -->

<!--   return(this_fig) -->
<!-- } -->




<!-- hist_POP = hist_plot(this_dat = combine_POP) -->
<!-- hist_OAK = hist_plot(this_dat = combine_OAK) -->
<!-- hist_IMP130 = hist_plot(this_dat = combine_IMP130) -->


<!-- ## POPLAR -->
<!-- umap_POP_bin = umap_plot(this_dat = combine_POP, fea = binned_density_fea) -->
<!-- umap_POP_spat = umap_plot(this_dat = combine_POP, fea = spat_fea) -->
<!-- umap_POP_comb = umap_plot(this_dat = combine_POP, fea = comb_fea) -->

<!-- ## OAK -->
<!-- umap_OAK_bin = umap_plot(this_dat = combine_OAK, fea = binned_density_fea) -->
<!-- umap_OAK_spat = umap_plot(this_dat = combine_OAK, fea = spat_fea) -->
<!-- umap_OAK_comb = umap_plot(this_dat = combine_OAK, fea = comb_fea) -->

<!-- ## IMPassion130 -->
<!-- umap_IMP130_bin = umap_plot(this_dat = combine_IMP130, fea = binned_density_fea) -->
<!-- umap_IMP130_spat = umap_plot(this_dat = combine_IMP130, fea = spat_fea) -->
<!-- umap_IMP130_comb = umap_plot(this_dat = combine_IMP130, fea = comb_fea) -->


<!-- ``` -->



<!-- ```{r} -->

<!-- library("gridExtra") -->

<!-- png("Fig3_new.png", width = 4000, height = 4500, res = 300) -->
<!-- # Arrange multiple ggplots and print the output -->
<!-- fig3 = grid.arrange(hist_POP, umap_POP_bin, umap_POP_spat, umap_POP_comb, -->
<!--                     hist_OAK, umap_OAK_bin, umap_OAK_spat, umap_OAK_comb, -->
<!--                     hist_IMP130, umap_IMP130_bin, umap_IMP130_spat, umap_IMP130_comb, -->
<!--                     ncol = 3, nrow = 4,  -->
<!--                     layout_matrix = cbind(c(1,2,3,4), c(5,6,7,8), c(9,10,11,12))) -->
<!-- print(fig3) -->

<!-- dev.off() -->


<!-- ``` -->

